### 2013-04-01 paper/paper.tex
paper draft 1

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2013}
\usepackage{times}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{paralist}
\defaultleftmargin{1em}{}{}{} % default is 2em

\usepackage[round]{natbib}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
{\large Chris Dyer$^1$ Manaal Faruqui$^1$ Noam Ordan$^2$ Nathan Schneider$^1$\\ Yulia Tsvetkov$^1$ Naama Twitto$^2$ Shuly Wintner$^2$}\\[-3em]
}

\author{
\\
$^1$Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
\And
\\
$^2$Department of Computer Science\\University of Haifa\\Haifa, Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%C.\ Dyer M.\ Faruqui N.\ Schneider Y.\ Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%N.\ Ordan N.\ Twitto S.\ Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%Chris Dyer\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%Manaal Faruqui\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{manaalfar@gmail.com}
%\And
%Noam Ordan\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{noam.ordan@gmail.com}
%\And
%Nathan Schneider\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{nathan@cmu.edu}
%\And
%Yulia Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{yulia.tsvetkov@gmail.com}
%\And
%Naama Twitto\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{naama.twitto@gmail.com}
%\And
%Shuly Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
}

\date{}

\begin{document}
\maketitle
\begin{abstract}
Given a dataset of English essays composed by non-native speakers, as
part of the TOEFL exam, we identify with high accuracy the native
language of the authors. We use standard text classification
techniques, but define sophisticated classifiers that are sensitive to
the specific patterns observed in the English of authors whose first
language is structurally different. We describe the various features
used for classification, as well as the settings of the classifier
that yielded the highest accuracy.
\end{abstract}

\section{Introduction}
\label{sec:intro}
The task we address in this work is identifying the native language
(\emph{L1}) of non-native English authors. More specifically, given a
dataset
\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR} of
short English essays, composed as part of the TOEFL exam (of English
as a foreign language) by authors whose native language is one out
of~11 possible languages (Arabic, Chinese, French, German, Hindi,
Italian, Japanese, Korean, Spanish, Telugu, and Turkish), our task is
to identify that language.

This task has a clear empirical motivation. Non-native speakers make
different errors when they write English, depending on their native
language \citep{swan2001learner}; understanding the different types of
errors is a prerequisite for correcting them
\citep{Leacock:2010:AGE:1855062}, and systems such as the one we
describe here can shed interesting light on such errors. Tutoring
applications can use our system to identify the native language of
students and offer better-targeted advice. Forensic linguistic
applications are sometimes required to determine the L1 of authors
\citep{estival-gaustad-pham-radford-hutchinson:2007:ALTA2007,estival2007author}. Additionally,
we believe that the task is interesting in and of itself, providing a
better understanding of non-native language. We are thus equally
interested in defining \emph{meaningful} features whose contribution
to the task can be linguistically interpreted.

We address the task as a multiway text-classification task; we specify
our methodology in Section~\ref{sec:methodology}. As in other author
attribution tasks \citep{joula:2006}, the choice of features for the
classifier is crucial; we discuss the features we define in
Section~\ref{sec:features}. We report our results in
Section~\ref{sec:results} and conclude with suggestions for future
research.

\section{Related work}
\label{sec:literature}
The task of L1 identification was introduced by
\citet{koppel2005automatically,koppel2005determining}, who work on the
International Corpus of Learner English \citep{icle}, which includes
texts written by students from Russia, the Czech Republic, Bulgaria,
France, and Spain. The texts lengths range from 500 to 850 words. The
classification method is a linear SVM, and features include 400
standard function words, 200 letter $n$-grams, 185 error types and 250
rare part-of-speech (POS) bi-grams. Ten-fold cross-validation results
on this dataset are 80\% accuracy.

The same experimental setup is assumed by
\citet{tsur-rappoport:2007:Cognitive-2007}, who are mostly interested
in testing the hypothesis that an author's choice of words in a second
language is influenced by the phonology of his or her L1. They confirm
this hypothesis by carefully analyzing the features used by
\citeauthor{koppel2005automatically}, controlling for potential
biases.

\citet{Wong-Dras:2009:ALTA2009,wong-dras:2011:EMNLP} are also
motivated by a linguistic hypothesis, namely that syntactic errors in
a text are influenced by the author's
L1. \citet{Wong-Dras:2009:ALTA2009} analyze three error types
statistically, and then add them as features in the same experimental
setup as above (using LIBSVM with a radial kernel for
classification). The error types are subject-verb disagreement,
noun-number disagreement and misuse of determiners. Addition of these
features does not improve on the results of
\citeauthor{koppel2005automatically}. \citet{wong-dras:2011:EMNLP}
further extend this work by adding as features horizontal slices of
parse trees, thereby capturing more syntactic structure. This improves
the results significantly, yielding 78\% accuracy compared with less
than 65\% using only lexical features.

\citet{kochmar2011identification} uses a different corpus, the
Cambridge Learner Corpus, in which texts are 200-400 word long, and
are authored by native speakers of five Germanic languages (German,
Swiss German, Dutch, Swedish and Danish) and five Romance languages
(French, Italian, Catalan, Spanish and Portuguese). Again, SVM is the
classification device. Features include POS $n$-grams, character
$n$-grams, phrase-structure rules (extracted from parse trees), and
two measures of error rate. The classifier is evaluated on its ability
to distinguish between pairs of closely-related L1s, and the results
are usually excellent.

A completely different approach is offered by
\citet{brooke2011native}. Since training corpora for this task are
rare, they use mainly L1 (blog) corpora. Given English word bi-grams
$\langle e_1,e_2\rangle$, they try to assess, for each L1, how likely
it is that an L1 bi-gram was translated literally by the author,
resulting in $\langle e_1,e_2\rangle$. Working with four L1s (French,
Spanish, Chinese, and Japanese), and evaluating on the International
Corpus of Learner English, the results are lower than 50\%.

Our dataset in this work is different, and consists of TOEFL essays
written by speakers of eleven different L1s
\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR},
distributed as part of the First Native Language Identification Shared
Task \citep{tetreault-blanchard-cahill:2013:BEA}. We use a plethora of
features; some of them are inspired by previous work outlined above,
but many are motivated by other author attribution tasks, in
particular identification of \emph{translationese}, the language of
translated texts \citep{vered:noam:shuly}.

\section{Methodology}
\label{sec:methodology}
Characteristics of the dataset. Development, train, test sets.

For classification we use \emph{creg}...

Pre-processing: POS-tagging, etc.

\section{Features}
\label{sec:features}
We define a large arsenal of features, our motivation being both to
improve the accuracy of classification and to be able to interpret the
characteristics of the language produced by speakers of different
L1s. In this section we define the features and motivate their use.%
\footnote{Whenever counts are mentioned, we use the log of the count
  as the feature.}  
While some of the features were used in the works surveyed in
Section~\ref{sec:literature}, many are novel, and are inspired by the
features used to identify translationese by \citet{vered:noam:shuly}.
We also report the accuracy of using each feature type, in isolation,
on the training set.

\begin{compactdesc}
\item[Character $n$-grams] The number of character 1-, 2-, and
  3-grams. 69.94\%.
\item[Frequent character $n$-grams] Only those character $n$-grams
  that are observed more than $m$ times in the corpus are
  considered. ???
\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
\item[Document length] The number of tokens in the text. 11.81\%.
\item[Pronouns] The number of each pronoun. 22.81\%.
\item[Punctuation] The number of each punctuation mark. 27.41\%.
\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the authors L1. We use the counts (???) of the first
  and last three words in each sentence as features. 53.03\%.
\item[Cohesive markers] These are function words (and short phrases)
  that have a strong discourse function in texts, contributing to its
  cohesiveness. 25.71\%.
\item[Cohesive verbs] ???. 22.85\%.
\item[Function words] The number of occurrences of each word from a
  pre-defined list of 100 most frequent words in English (excluding
  punctuation). 42.47\%.
\item[Contextual function words, bigrams] Pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. 62.79\%
\item[Contextual function words, trigrams] Same as above, but counting
  3-grams consisting of two function words and the POS tag of the
  third word in the 3-gram. 62.32\%.
\item[Lemmas] The number of each of the most frequent lemmas in the
  text. ???. 58.95\%.
\item[Prompt] Conjunction of the character $n$-gram features defined
  above with the prompt; since the prompt contributes information on
  the domain, it is likely that some words (and, hence, character
  sequences) will occur more frequently with some prompts than with
  others. 65.09\%.
\item[Misspelling features] ???. 37.29\%.
\item[Brown] ???
\item[Restored] ???
\end{compactdesc}

\section{Results}
\label{sec:results}

\section{Conclusion}
\label{sec:conclusion}

\section*{Acknowledgments}
This research was supported by a grant from the Israeli Ministry of
Science and Technology.

\clearpage

\bibliography{l1id}
\bibliographystyle{plainnat}

\end{document}

### 2013-04-02 paper/paper.tex
feature sections

@@
 \documentclass[11pt,letterpaper]{article}
+\usepackage[linkcolor=blue]{hyperref}	% must precede ACL style
+\usepackage{relsize} % relative font sizes (e.g. \smaller). must precede ACL style
 \usepackage{naaclhlt2013}
@@
 \usepackage{latexsym}
-\usepackage{hyperref}
+
+\usepackage{amsmath,amsfonts,eucal,amsbsy,amsthm,amsopn,amssymb}
+
+\usepackage{txfonts}
+\usepackage[scaled]{beramono}
+\usepackage[T1]{fontenc}
+
 \usepackage{paralist}
@@
 
+% Author comments
+\usepackage{color}
+\usepackage{bm}
+\definecolor{orange}{rgb}{1,0.5,0}
+\definecolor{mdgreen}{rgb}{0,0.6,0}
+\definecolor{dkblue}{rgb}{0,0,0.5}
+\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
+\definecolor{slate}{rgb}{0.25,0.25,0.4}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{purple}{rgb}{0.7,0,1.0}
+\newcommand{\ensuretext}[1]{#1}
+\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
+\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
+\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
+\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
+\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
+\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
+%\newcommand{\arkcomment}[3]{}
+\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
+\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
+\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
+\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
+\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
+\newcommand{\w}{\mathbf{w}}
+\newcommand{\g}{\mathbf{g}}
+\newcommand{\f}{\mathbf{f}}
+\newcommand{\x}{\boldsymbol{x}}
+\newcommand{\y}{\boldsymbol{y}}
+\newcommand{\cost}{c}
+
+\newcommand{\Sref}[1]{\S\ref{#1}}
+\newcommand{\fref}[1]{figure~\ref{#1}}
+\newcommand{\Fref}[1]{Figure~\ref{#1}}
+\newcommand{\tref}[1]{table~\ref{#1}}
+\newcommand{\Tref}[1]{Table~\ref{#1}}
+
+% special macros
+
+\newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
+
 \title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
-{\large Chris Dyer$^1$ Manaal Faruqui$^1$ Noam Ordan$^2$ Nathan Schneider$^1$\\ Yulia Tsvetkov$^1$ Naama Twitto$^2$ Shuly Wintner$^2$}\\[-3em]
+{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
 }
@@
 \\
-$^1$Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
+$^\ast$Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
 \And
 \\
-$^2$Department of Computer Science\\University of Haifa\\Haifa, Israel\\\texttt{shuly@cs.haifa.ac.il}
+$^\dagger$Department of Computer Science\\University of Haifa\\Haifa, Israel\\\texttt{shuly@cs.haifa.ac.il}
 %
@@
 We address the task as a multiway text-classification task; we specify
-our methodology in Section~\ref{sec:methodology}. As in other author
+our methodology in \Sref{sec:methodology}. As in other author
 attribution tasks \citep{joula:2006}, the choice of features for the
 classifier is crucial; we discuss the features we define in
-Section~\ref{sec:features}. We report our results in
-Section~\ref{sec:results} and conclude with suggestions for future
+\Sref{sec:features}. We report our results in
+\Sref{sec:results} and conclude with suggestions for future
 research.
@@
 
-\section{Features}
-\label{sec:features}
+\section{Model Overview}
+%\label{sec:features}
+
+\nss{I think we should break this up into sections by feature group (below). 
+Here we can talk about learning and regularization and give a high-level overview 
+of features.}
+
 We define a large arsenal of features, our motivation being both to
@@
 While some of the features were used in the works surveyed in
-Section~\ref{sec:literature}, many are novel, and are inspired by the
+\Sref{sec:literature}, many are novel, and are inspired by the
 features used to identify translationese by \citet{vered:noam:shuly}.
@@
 
+\section{Main Features}\label{sec:mainfeats}
+
+These four feature groups form the core of our model.
+
+\subsection{\feat{POS}: part-of-speech sequences}
+
+\subsection{\feat{FreqChar}: frequent character $n$-grams}
+
+\subsection{\feat{CharPrompt}: character $n$-grams paired with the prompt ID}
+
+\subsection{\feat{Brown}: Brown clusters}
+
+\section{Additional Features}
+
+Each of these adds a small number of parameters to the model. 
+We report the empirical improvement that each of these brings 
+independently when added to the main features (\Sref{sec:mainfeats}).
+The full model combines all features.
+
+\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}}
+
+\subsection{\feat{DocLen}: Document length in tokens}
+
+\subsection{\feat{Misspell}: Spelling correction edits}
+
+\subsection{\feat{Position}: \nss{?}}
+
+\subsection{\feat{Pron}: pronouns\nss{?}}
+
+\subsection{\feat{PsvRatio}: Ratio of passive to active voice verbs\nss{or is it the proportion of passive verbs?}}
+
+\subsection{\feat{Punct}: Count of each punctuation mark}
+
+\subsection{\feat{Restore}: LM-restored function words}
+
+\subsection{Discarded Features}
+
+\nss{things that didn't help in our preliminary experiments}
+
 \section{Results}

### 2013-04-03 paper/paper.tex
Noam's comments

@@
   that are observed more than $m$ times in the corpus are
-  considered. ???
+  considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
 \item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
@@
   and last three words in each sentence as features. 53.03\%.
-\item[Cohesive markers] These are function words (and short phrases)
-  that have a strong discourse function in texts, contributing to its
-  cohesiveness. 25.71\%.
-\item[Cohesive verbs] ???. 22.85\%.
+\item[Cohesive markers] These are 40 function words (and short phrases)
+  that have a strong discourse function in texts \nt{such as 'however', 'becuase', 'in fact' etc}, contributing to its
+  cohesiveness. 25.71\%. \nt{Translators tend to spell out implicit utterances and render them explicitly in the target text (REFERENCE TO BLUM-KULKA); MAYBE APPEND THE LIST IN THE END?} 
+\item[Cohesive verbs] \nt{This is a list of manually compiled verbs that serve, like `cohesive markers' to spell out implicit utterances; they include, among others, `indicating', `implying' and `containing'.
+Same, consider appending the list}.
+22.85\%.
 \item[Function words] The number of occurrences of each word from a
-  pre-defined list of 100 most frequent words in English (excluding
+  pre-defined list of 100 \nt{did you use only 100? it should be 400 and the reference should be to Koppel and Ordan} most frequent words in English (excluding
   punctuation). 42.47\%.
@@
 \item[Contextual function words, trigrams] Same as above, but counting
-  3-grams consisting of two function words and the POS tag of the
-  third word in the 3-gram. 62.32\%.
-\item[Lemmas] The number of each of the most frequent lemmas in the
+  \nt{2- or} 3-grams consisting of one or two function words (respectively) and the POS tag of the third word \nt{character?} in the \nt{2- or} 3-gram. 62.32\%.
+\item[Lemmas] \nt{these should be actually `stems' as produced by the Stanford tagger} The number of each of the most frequent lemmas in the
   text. ???. 58.95\%.
@@
 
-\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}}
+\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}} \nt{yes}
 
@@
 
-\subsection{\feat{Pron}: pronouns\nss{?}}
+\subsection{\feat{Pron}: pronouns\nss{?}} \nt{A list of 25 pronouns in English, again, append list}
 

### 2013-04-05 analysis/split_n_sort.py
split to languages, sort by feature weights

@@ -1,0 +1,36 @@
+#!/bin/env python2.7
+
+import sys, collections
+
+LABELS = ["ARA", "CHI", "FRE", "GER", "HIN", "ITA", "JPN", "KOR", "SPA", "TEL", "TUR"]
+
+def Split(in_file):
+  weights = collections.defaultdict(list)
+  out_files = {}
+
+  for line in (in_file):
+    tok = line.strip().split("\t")
+    if len(tok) != 3:
+      continue 
+    weights[tok[0]].append((float(tok[2]), tok[1]))
+
+  for label in LABELS:
+    out_files[label] = open(label+".feat", "w")
+
+  for label in LABELS:
+    features = sorted(weights[label], key=lambda tup: abs(tup[0]), reverse = True) 
+    for v, f in features:
+      out_files[label].write("%f\t%s\n" % (v,f))
+
+def main(args):
+  usage = './split_n_sort.py in_weights'
+  if len(args) < len(usage.split()) - 1:
+    print 'usage:', usage
+    sys.exit(1)
+
+  Split(open(args[1]))
+
+if __name__ == '__main__':
+  main(sys.argv)
+
+

### 2013-04-06 paper/paper.tex
restored feature

@@
   words in a sentence is highly constrained, and may be significantly
-  influenced by the authors L1. We use the counts (???) of the first
+  influenced by the authors L1. We use the counts (???)\yt{counts for first two and last three words before the period} of the first
   and last three words in each sentence as features. 53.03\%.
@@
 \item[Function words] The number of occurrences of each word from a
-  pre-defined list of 100 \nt{did you use only 100? it should be 400 and the reference should be to Koppel and Ordan} most frequent words in English (excluding
+  pre-defined list of 100 \nt{did you use only 100?
+it should be 400 and the reference should be to Koppel and Ordan} \yt{we used 100.
+differences between 100 and >100 were insignificant} most frequent words in English (excluding
   punctuation). 42.47\%.
@@
 \item[Brown] ???
-\item[Restored] ???
+\item[Restored] \yt{Counts of substitutions, deletions and insertions of predefined tags that we restored in essays edited with a spelling  corrector and missing all these tags.
+We define three types of tags: (1) punctuation marks (same list as for punctuation feature), (2) function words (WH-words, prepositions, conjunctions, articles, auxiliary verbs, quantifiers, personal pronouns, possessive pronouns, quantified pronouns), (3) cohesion verbs (lemma, present contiguous/progressive and present simple for each verb).
+We first remove these tags from texts and then recover the most likely hidden tags in a sequence of words, according to an N-gram language model trained on all essays in the training corpus corrected with a spell checker and containing both words and hidden tags.
+This feature should capture specific words or punctuation marks that are consistently omitted (deletions), or misused (insertions, substitutions).
+To restore hidden tags we use hidden-ngram utility provided in SRILM toolkit\footnote{http://www.speech.sri.com/projects/srilm/manpages/hidden-ngram.1.html} (ref to SRILM).
+47.67\%}
+
 \end{compactdesc}

### 2013-04-06 paper/paper.tex
results from feature combination experiments

@@
 
+\begin{table}\small\centering
+\begin{tabular}{lrcc}
+\textbf{Feature Group} & \multicolumn{1}{c}{\textbf{\# Params}} & \textbf{Accuracy (\%)} & \textbf{$\ell_2$} \\
+\hline
+\feat{POS} & 540,947 & 55.18 & 1.0 \\
++ \feat{FreqChar} & 1,036,871 & 79.55 & 1.0 \\ 
+\quad + \feat{CharPrompt} & 2,111,175 & 79.82 & 1.0 \\ 
+\qquad + \feat{Brown} & 5,664,461 & 81.09 & 1.0 \\
+\end{tabular}
+\caption{Dev set accuracy with \textsc{main} feature groups, added cumulatively. 
+The number of parameters is always a multiple of 11 (the number of classes). 
+Only $\ell_2$ regularization was used for these experiments; 
+the penalty was tuned on the dev set as well.}\label{tbl:mainfeats}
+\end{table}
+
+\begin{table}\small\centering
+\begin{tabular}{lrcc}
+\textbf{Feature Group} & \multicolumn{1}{c}{\textbf{\# Params}} & \textbf{Accuracy (\%)} & \textbf{$\ell_2$} \\
+\hline
+\textsc{main} + \feat{Position} & 6,153,015 & 81.00 & 1.0 \\
+\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 & 1.0 \\
+\textsc{main} & 5,664,461 & 81.09 & 1.0 \\
+\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09 & 1.0 \\
+\textsc{main} + \feat{Pron} & 5,664,736 & 81.09 & 1.0 \\
+\textsc{main} + \feat{Punct} & 5,664,604 & 81.09 & 1.0 \\
+\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27 & 5.0 \\
+\textsc{main} + \feat{Restore} & 5,682,589 & 81.36 & 5.0 \\
+\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 & 1.0 \\
+\end{tabular}
+\caption{Dev set accuracy with \textsc{main} features plus additional feature groups, added independently. 
+$\ell_2$ regularization was tuned as in \tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
+configuration; more careful tuning might produce slightly better accuracy).
+Results are sorted by accuracy; only three groups exhibited independent improvements over the \textsc{main} feature set.}\label{tbl:addfeats}
+\end{table}
+
 \section{Conclusion}

### 2013-04-06 paper/paper.tex
confusion matrix; POS tagger

@@
 \defaultleftmargin{1em}{}{}{} % default is 2em
+
+\usepackage{array}
 
@@
 \end{abstract}
+
+\nss{shouldn't we use the official bib style file instead of natbib?}
 
@@
   considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
-\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
+\item[POS $n$-grams] All essays were tagged with the Stanford part-of-speech tagger \citep{toutanova-03}.
+Features were extracted to count every POS 1-, 2-, and 3-gram in each document. 53.92\%.
 \item[Document length] The number of tokens in the text. 11.81\%.
@@
 
+\begin{table*}\small\centering
+\begin{tabular}{>{\bf}l|r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r|ccc} %from the email sent by the organizers
+	& \bf ARA & \bf CHI & \bf FRE & \bf GER & \bf HIN & \bf ITA & \bf JPN & \bf KOR & \bf SPA & \bf TEL & \bf TUR & \bf Precision (\%) & \bf Recall (\%) & \bf $F_1$ (\%) \\
+\hline
+ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0 & 80.4 \\
+CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0 & 84.2 \\
+FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0 & 83.5 \\
+\hline
+GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0 & 90.3 \\
+HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0 & 75.9 \\
+ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0 & 84.5 \\
+\hline
+JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 & 82.5 \\
+KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0 & 80.6 \\
+SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0 & 77.6 \\
+\hline
+TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0 & 78.9 \\
+TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0 & 78.4 \\
+\end{tabular}
+\caption{Official test set confusion matrix with the full model. \nss{which direction is predicted vs. gold?}
+Accuracy is 81.5\%.}\label{tbl:matrix}
+\end{table*}
+
 \section{Conclusion}
@@
 This research was supported by a grant from the Israeli Ministry of
-Science and Technology.
+Science and Technology.\nss{anything from the CMU side?}
 

### 2013-04-06 paper/paper.tex
from shuly

@@
 
-\nss{shouldn't we use the official bib style file instead of natbib?}
-
 \section{Introduction}
@@
 (\emph{L1}) of non-native English authors. More specifically, given a
-dataset
-\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR} of
-short English essays, composed as part of the TOEFL exam (of English
-as a foreign language) by authors whose native language is one out
-of~11 possible languages (Arabic, Chinese, French, German, Hindi,
-Italian, Japanese, Korean, Spanish, Telugu, and Turkish), our task is
-to identify that language.
+dataset of short English essays
+\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR},
+composed as part of the \emph{Test of English as a Foreign Language
+  (TOEFL)} by authors whose native language is one out of~11 possible
+languages (Arabic, Chinese, French, German, Hindi, Italian, Japanese,
+Korean, Spanish, Telugu, and Turkish), our task is to identify that
+language.
 
@@
 
-For classification we use \emph{creg}...
+For classification we use \emph{creg}... \nss{Here we can talk about
+  learning and regularization and give a high-level overview of
+  features.}
 
-Pre-processing: POS-tagging, etc.
+All essays were tagged with the Stanford part-of-speech tagger
+\citep{toutanova-03}. We did not parse the dataset.
 
 \section{Model Overview}
-%\label{sec:features}
-
-\nss{I think we should break this up into sections by feature group (below). 
-Here we can talk about learning and regularization and give a high-level overview 
-of features.}
-
+\label{sec:features}
 We define a large arsenal of features, our motivation being both to
@@
 characteristics of the language produced by speakers of different
-L1s. In this section we define the features and motivate their use.%
-\footnote{Whenever counts are mentioned, we use the log of the count
-  as the feature.}  
+L1s.
+
+\subsection{Motivation}
 While some of the features were used in the works surveyed in
@@
 features used to identify translationese by \citet{vered:noam:shuly}.
-We also report the accuracy of using each feature type, in isolation,
-on the training set.
+We begin by motivating our choice of features.
 
 \begin{compactdesc}
-\item[Character $n$-grams] The number of character 1-, 2-, and
-  3-grams. 69.94\%.
-\item[Frequent character $n$-grams] Only those character $n$-grams
-  that are observed more than $m$ times in the corpus are
-  considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
-\item[POS $n$-grams] All essays were tagged with the Stanford part-of-speech tagger \citep{toutanova-03}.
-Features were extracted to count every POS 1-, 2-, and 3-gram in each document. 53.92\%.
-\item[Document length] The number of tokens in the text. 11.81\%.
-\item[Pronouns] The number of each pronoun. 22.81\%.
-\item[Punctuation] The number of each punctuation mark. 27.41\%.
-\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
+\item[POS $n$-grams] Part-of-speech $n$-grams were used in various
+  text-classification tasks.
+\item[Prompt] Since the prompt contributes information on the domain,
+  it is likely that some words (and, hence, character sequences) will
+  occur more frequently with some prompts than with others. We
+  therefore use the prompt ID in conjunction with other features.
+\item[Document length] The number of tokens in the text is highly
+  correlated with the author's level of fluency, which in turn is
+  correlated with the author's L1.
+\item[Pronouns] The use of pronoun varies greatly among different
+  authors. We use the same list of~25 English pronouns that
+  \citet{vered:noam:shuly} use for identifying translationese.
+\item[Punctuation] Similarly, different languages use punctuation
+  differently, and we expect this to taint the use of punctuation in
+  non-native texts.
+\item[Passives] English uses passive voice more frequently than other
+  languages. Again, the use of passives in L2 can be correlated with
+  the author's L1.
 \item[Positional token frequency] The choice of the first and last few
   words in a sentence is highly constrained, and may be significantly
-  influenced by the authors L1. We use the counts (???)\yt{counts for first two and last three words before the period} of the first
-  and last three words in each sentence as features. 53.03\%.
-\item[Cohesive markers] These are 40 function words (and short phrases)
-  that have a strong discourse function in texts \nt{such as 'however', 'becuase', 'in fact' etc}, contributing to its
-  cohesiveness. 25.71\%. \nt{Translators tend to spell out implicit utterances and render them explicitly in the target text (REFERENCE TO BLUM-KULKA); MAYBE APPEND THE LIST IN THE END?} 
-\item[Cohesive verbs] \nt{This is a list of manually compiled verbs that serve, like `cohesive markers' to spell out implicit utterances; they include, among others, `indicating', `implying' and `containing'.
-Same, consider appending the list}.
-22.85\%.
-\item[Function words] The number of occurrences of each word from a
-  pre-defined list of 100 \nt{did you use only 100?
-it should be 400 and the reference should be to Koppel and Ordan} \yt{we used 100.
-differences between 100 and >100 were insignificant} most frequent words in English (excluding
-  punctuation). 42.47\%.
-\item[Contextual function words, bigrams] Pairs consisting of a
+  influenced by the author's L1.
+\item[Cohesive markers] These are 40 function words (and short
+  phrases) that have a strong discourse function in texts (`however',
+  `because', `in fact', etc.) Translators tend to spell out implicit
+  utterances and render them explicitly in the target text
+  \citep{Blum-Kulka:1986}. We use the list
+  of~\citet{vered:noam:shuly}.
+\item[Cohesive verbs] This is a list of manually compiled verbs that
+  are used, like cohesive markers, to spell out implicit utterances
+  (`indicate', `imply', `contain', etc.)
+\item[Function words] Frequent tokens, which are mostly function
+  words, have been used successfully for various text classification
+  tasks. \citet{koppel-ordan:2011:ACL-HLT2011} define a list of 400
+  such words, of which we only use~100 (using the entire list was not
+  significantly different).
+\item[Contextual function words] To further capitalize on the ability
+  of function words to discriminate, we define pairs consisting of a
   function word from the list mentioned above, along with the POS tag
@@
   and the preposition or particle immediately to their right, or nouns
-  and the determiner that precedes them. 62.79\%
-\item[Contextual function words, trigrams] Same as above, but counting
-  \nt{2- or} 3-grams consisting of one or two function words (respectively) and the POS tag of the third word \nt{character?} in the \nt{2- or} 3-gram. 62.32\%.
-\item[Lemmas] \nt{these should be actually `stems' as produced by the Stanford tagger} The number of each of the most frequent lemmas in the
-  text. ???. 58.95\%.
-\item[Prompt] Conjunction of the character $n$-gram features defined
-  above with the prompt; since the prompt contributes information on
-  the domain, it is likely that some words (and, hence, character
-  sequences) will occur more frequently with some prompts than with
-  others. 65.09\%.
-\item[Misspelling features] ???. 37.29\%.
-\item[Brown] ???
-\item[Restored] \yt{Counts of substitutions, deletions and insertions of predefined tags that we restored in essays edited with a spelling  corrector and missing all these tags.
-We define three types of tags: (1) punctuation marks (same list as for punctuation feature), (2) function words (WH-words, prepositions, conjunctions, articles, auxiliary verbs, quantifiers, personal pronouns, possessive pronouns, quantified pronouns), (3) cohesion verbs (lemma, present contiguous/progressive and present simple for each verb).
-We first remove these tags from texts and then recover the most likely hidden tags in a sequence of words, according to an N-gram language model trained on all essays in the training corpus corrected with a spell checker and containing both words and hidden tags.
-This feature should capture specific words or punctuation marks that are consistently omitted (deletions), or misused (insertions, substitutions).
-To restore hidden tags we use hidden-ngram utility provided in SRILM toolkit\footnote{http://www.speech.sri.com/projects/srilm/manpages/hidden-ngram.1.html} (ref to SRILM).
-47.67\%}
-
+  and the determiner that precedes them. We also define 3-grams
+  consisting of one or two function words and the POS tag of the third
+  word in the 3-gram.
+\item[Lemmas] The content of the text is not considered a good
+  indication of the author's L1, but many text categorization tasks
+  use lemmas (more precisely, the stems produced by the tagger) as
+  features approximating the content.
+\item[Misspelling features] Clearly, the spelling errors that learners
+  make in English depend on the phonological properties of their
+  L1. \sw{???}
+\item[Restored tags] We focus on three important token classes defined
+  above: punctuation marks, function words and cohesive verbs. We
+  first remove words in these classes from the texts, and then recover
+  the most likely hidden POS tags in a sequence of words, according to
+  an $n$-gram language model trained on all essays in the training
+  corpus corrected with a spell checker and containing both words and
+  hidden tags. This feature should capture specific words or
+  punctuation marks that are consistently omitted (deletions), or
+  misused (insertions, substitutions). To restore hidden tags we use
+  the \texttt{hidden-ngram} utility provided in SRILM
+  \citep{stolcke02srilm}.
+\item[Brown clusters] \sw{???}
 \end{compactdesc}
 
-\section{Main Features}\label{sec:mainfeats}
+\subsection{Main Features}
+\label{sec:mainfeats}
+First, we use the following four feature types as the core of our
+model.  Whenever counts are mentioned, we use the log of the count as
+the feature.  We report the accuracy of using each feature type, in
+isolation, on the training set.
 
-These four feature groups form the core of our model.
+\begin{compactdesc}
+\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
+  to count every POS 1-, 2-, and 3-gram in each
+  document. 53.92\%. \sw{But the table says 55.18}
+\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
+  with character $n$-grams: The number of character 1-, 2-, and
+  3-grams. This yielded 69.94\% accuracy.  We then refined the feature
+  to include only those character $n$-grams that are observed more
+  than $m$ times in the corpus are considered. \sw{$n$ ranges from~1
+    to~4, and $m$ is set to~???. 74.12\%}
+\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
+  features defined above with the prompt ID. 65.09\%.
+\item[\feat{Brown}] Brown clusters. \sw{???}
+\end{compactdesc}
+\noindent
+The accuracy of the classifier on the development set using these four
+feature types is reported in \Tref{tbl:mainfeats}.
 
-\subsection{\feat{POS}: part-of-speech sequences}
-
-\subsection{\feat{FreqChar}: frequent character $n$-grams}
-
-\subsection{\feat{CharPrompt}: character $n$-grams paired with the prompt ID}
-
-\subsection{\feat{Brown}: Brown clusters}
-
-\section{Additional Features}
-
-Each of these adds a small number of parameters to the model. 
-We report the empirical improvement that each of these brings 
-independently when added to the main features (\Sref{sec:mainfeats}).
-The full model combines all features.
-
-\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}} \nt{yes}
-
-\subsection{\feat{DocLen}: Document length in tokens}
-
-\subsection{\feat{Misspell}: Spelling correction edits}
-
-\subsection{\feat{Position}: \nss{?}}
-
-\subsection{\feat{Pron}: pronouns\nss{?}} \nt{A list of 25 pronouns in English, again, append list}
-
-\subsection{\feat{PsvRatio}: Ratio of passive to active voice verbs\nss{or is it the proportion of passive verbs?}}
-
-\subsection{\feat{Punct}: Count of each punctuation mark}
-
-\subsection{\feat{Restore}: LM-restored function words}
-
-\subsection{Discarded Features}
-
-\nss{things that didn't help in our preliminary experiments}
-
-\section{Results}
-\label{sec:results}
-
-\begin{table}\small\centering
+\begin{table}[hbt]
+\small\centering
 \begin{tabular}{lrcc}
@@
   Only $\ell_2$ regularization was used for these experiments; 
-the penalty was tuned on the dev set as well.}\label{tbl:mainfeats}
+  the penalty was tuned on the dev set as well.}
+\label{tbl:mainfeats}
 \end{table}
 
-\begin{table}\small\centering
+\subsection{Additional Features}
+To the basic set of features we now add more specific,
+linguistically-motivated features, each adding a small number of
+parameters to the model.  As above, we indicate the accuracy of each
+feature type in isolation.
+
+\begin{compactdesc}
+\item[\feat{DocLen}] Document length in tokens. 11.81\%.
+\item[\feat{Punct}] Counts of each punctuation mark. 27.41\%.
+\item[\feat{Pron}] Counts of each pronoun. 22.81\%.
+\item[\feat{Position}] Positional token frequency. We use the counts
+  for the first two and last three words before the period in each
+  sentence as features. 53.03\%.
+\item[\feat{PsvRatio}] The proportion of passive verbs out of all
+  verbs. 12.26\%.
+\item[\feat{CxtFxn}] Contextual function words. Bi-grams yield
+  62.79\%, tri-gram 62.32\%.
+\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%.
+\item[\feat{Restore}] Counts of substitutions, deletions and
+  insertions of predefined tags that we restored in the texts. 47.67\%
+\end{compactdesc}
+\noindent
+\Tref{tbl:addfeats} reports the empirical improvement that each of
+these brings independently when added to the main features
+(\Sref{sec:mainfeats}).
+
+\begin{table}[hbt]
+\small\centering
 \begin{tabular}{lrcc}
@@
 \caption{Dev set accuracy with \textsc{main} features plus additional feature groups, added independently. 
-$\ell_2$ regularization was tuned as in \tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
+$\ell_2$ regularization was tuned as in \Tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
 configuration; more careful tuning might produce slightly better accuracy).
-Results are sorted by accuracy; only three groups exhibited independent improvements over the \textsc{main} feature set.}\label{tbl:addfeats}
+Results are sorted by accuracy; only three groups exhibited independent improvements over the \textsc{main} feature set.}
+\label{tbl:addfeats}
 \end{table}
 
-\begin{table*}\small\centering
+\subsection{Discarded Features}
+We also tried several other feature types that did not improve the
+accuracy of the classifier on the development set.
+\begin{compactdesc}
+\item[Cohesive markers] Counts of each cohesive marker. 25.71\%.
+\item[Cohesive verbs] Counts of each cohesive verb. 22.85\%.
+\item[Function words] Counts of function words. 42.47\%. This feature
+  is subsumed by the highly discriminative \feat{CxtFxn} feature.
+\end{compactdesc}
+
+\section{Results}
+\label{sec:results}
+The full model that we used to classify the test set combines all
+features listed in \Tref{tbl:addfeats}. Using all these features, the
+accuracy on the development set is \sw{???}, and on the test set it
+is~81.5\%. \Tref{tbl:matrix} lists the confusion matrix on the test
+set, as well as precision, recall and $F_1$-score for each L1.
+
+\begin{table*}[hbt]
+\small\centering
 \begin{tabular}{>{\bf}l|r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r|ccc} %from the email sent by the organizers
@@
 \caption{Official test set confusion matrix with the full model. \nss{which direction is predicted vs. gold?}
-Accuracy is 81.5\%.}\label{tbl:matrix}
+Accuracy is 81.5\%.}
+\label{tbl:matrix}
 \end{table*}
+
+\sw{Analysis? Error analysis? Observations?}
 
@@
 
-\clearpage
+%\clearpage
 

### 2013-04-06 paper/paper.tex
updated Restored

@@
   first remove words in these classes from the texts, and then recover
-  the most likely hidden POS tags in a sequence of words, according to
+  the most likely hidden tokens \yt{To Shuly: I removed 'POS'.
+We recover words, not POS tags, I used the word 'tags' to distinguish between words to recover and all other words.
+Probably the word 'tag' is misleading, I changed it to 'token'} in a sequence of words, according to
   an $n$-gram language model trained on all essays in the training
   corpus corrected with a spell checker and containing both words and
-  hidden tags. This feature should capture specific words or
+  hidden tokens. This feature should capture specific words or
   punctuation marks that are consistently omitted (deletions), or
-  misused (insertions, substitutions). To restore hidden tags we use
+  misused (insertions, substitutions). To restore hidden tokens we use
   the \texttt{hidden-ngram} utility provided in SRILM
@@
 \item[\feat{Restore}] Counts of substitutions, deletions and
-  insertions of predefined tags that we restored in the texts. 47.67\%
+  insertions of predefined tokens that we restored in the texts. 47.67\%
 \end{compactdesc}

### 2013-04-06 paper/paper.tex
tweaks

@@
   authors. We use the same list of~25 English pronouns that
-  \citet{vered:noam:shuly} use for identifying translationese.
+  \citet{vered:noam:shuly} use for identifying translationese.\nss{subsumed by contextual function words, right?}
 \item[Punctuation] Similarly, different languages use punctuation
   differently, and we expect this to taint the use of punctuation in
-  non-native texts.
+  non-native texts.\nss{subsumed by char n-grams, right?}
 \item[Passives] English uses passive voice more frequently than other
@@
 \caption{Official test set confusion matrix with the full model. \nss{which direction is predicted vs. gold?}
-Accuracy is 81.5\%.}
-\label{tbl:matrix}
+The largest class of errors was predicting Telugu where the correct label was Hindi\nss{or vice versa?}---this happened 18 times. 
+Accuracy is 81.5\%.}\label{tbl:matrix}
 \end{table*}

### 2013-04-07 paper/paper.tex
merge analysis

--- 2013-04-06 paper/paper.tex
@@
 \usepackage{latexsym}
+\usepackage{tipa}
 
@@
 \newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
+\newcommand{\textnl}{\textsl}
 
@@
 The task we address in this work is identifying the native language
-(\emph{L1}) of non-native English authors. More specifically, given a
+(\emph{L1}) of non-native English (\emph{L2}) authors. More specifically, given a
 dataset of short English essays
@@
   correlated with the author's L1.
-\item[Pronouns] The use of pronoun varies greatly among different
+\item[Pronouns] The use of pronouns varies greatly among different
   authors. We use the same list of~25 English pronouns that
@@
   differently, and we expect this to taint the use of punctuation in
-  non-native texts.
+  non-native texts. Of course, character $n$-grams subsume this feature.
 \item[Passives] English uses passive voice more frequently than other
@@
 \item[Cohesive markers] These are 40 function words (and short
-  phrases) that have a strong discourse function in texts (`however',
-  `because', `in fact', etc.) Translators tend to spell out implicit
+  phrases) that have a strong discourse function in texts (\textnl{however},
+  \textnl{because}, \textnl{in fact}, etc.) Translators tend to spell out implicit
   utterances and render them explicitly in the target text
@@
   are used, like cohesive markers, to spell out implicit utterances
-  (`indicate', `imply', `contain', etc.)
+  (\textnl{indicate}, \textnl{imply}, \textnl{contain}, etc.)
 \item[Function words] Frequent tokens, which are mostly function
@@
   such words, of which we only use~100 (using the entire list was not
-  significantly different).
+  significantly different). Note that pronouns are included in this list.
 \item[Contextual function words] To further capitalize on the ability
@@
   first remove words in these classes from the texts, and then recover
-  the most likely hidden tokens \yt{To Shuly: I removed 'POS'.
-We recover words, not POS tags, I used the word 'tags' to distinguish between words to recover and all other words.
-Probably the word 'tag' is misleading, I changed it to 'token'} in a sequence of words, according to
+  the most likely hidden tokens in a sequence of words, according to
   an $n$-gram language model trained on all essays in the training
@@
 set, as well as precision, recall and $F_1$-score for each L1.
+The largest class of errors was predicting Telugu where the correct label 
+was Hindi\nss{or vice versa?}---this happened 18 times.
 
@@
 
-\sw{Analysis? Error analysis? Observations?}
+Production of L2 texts, not unlike translating from L1 to L2, involves
+a tension between the imposing models of L1 (and the source text), on
+the one hand, and a set of cognitive constraints resulting from the
+efforts to generate the target text, on the other. The former is
+called \emph{interference} in Translation Studies \citep{Toury:1995}
+and \emph{interlanguage} in second language acquisition
+\citep{Selinker1972}.
+
+\citet{vered:noam:shuly} designed 32 classifiers to test the validity
+of the forces acting on translated texts, and found that interference
+consistently yielded the best performing classifiers. And indeed, in
+this work too, which replicates some of their classifiers, we find
+again that fingerprints of the source language are dominant in the
+makeup of L2 texts.
+
+The main difference, however, between texts translated by
+professionals and the texts we address here, is that more often than
+not professional translators translate into their mother tongue,
+whereas L2 writers write out of their mother tongue by definition. So
+interference is ever more exaggerated in their case, for example, also
+phonologically \citep{tsur-rappoport:2007:Cognitive-2007}.
+
+We illustrate this with some examples from Arabic native speakers. The
+character sequence \textnl{alot} is overrepresented in Arabic L2
+texts. Arabic has no indefinite article and we speculate that Arabic
+speakers conceive \textnl{a lot} as a single word; the Arabic
+equivalent for \textnl{a lot} is used adverbially like an \textnl{-ly}
+suffix in English. For the same reason, another prominent feature is a
+missing definite article before nouns and adjectives . Additionally,
+Arabic, being an Abjad language, rarely indicates vowels, and indeed
+we find many missing \textnl{e}-s and \textnl{i}-s in the texts of
+Arabic speakers. Phonologically, because Arabic conflates
+/\textipa{I}/ and /\textipa{@}/ into /i/ (at least in Modern Standard
+Arabic), we see that many \textnl{e}-s are indeed substituted for
+\textnl{i}-s in these texts.
+
+German overuses hyphens in two interesting ways. German can
+notoriously use relative clauses freely, and such constructions
+frequently occur between hyphens in the dataset, as in \textnl{any
+  given rational being -- let us say Immanual Kant -- we find
+  that}. Another overuse of hyphens stems from compounding, another
+facet of German, for example in \textnl{well-known},
+\textnl{community-help}, \textnl{spare-time}, \textnl{football-club},
+etc. Many of these reflect an effort to both connect and separate
+connected forms in the original (e.g., \textnl{Fussballklub}, which in
+English would be more naturally rendered as \textnl{football club}).
+Another unexpected feature of German is a frequent substitution of the
+letter \textnl{y} for \textnl{z} (and vice versa), most probably
+triggered by their switched positions on German keyboards.
+
+The word \textnl{that} occurs more frequently in the texts of German
+L1 speakers, perhaps because in English it is optional in relative
+clauses whereas in German it is not.  Last, \textnl{often} is
+overused; being a cognate of the German \textnl{oft} it is not
+cognitively expensive to retrieve it. Spanish, on the other hand,
+literally translates \textnl{muchas veces} into \textnl{many times},
+which is similarly overused on the dataset. \sw{any Spanish speaker
+  who could validate this expression?}
+
+Other informative features include substitutions of \textnl{r}-s and
+\textnl{l}-s in the texts of Japanese authors, for obvious reasons;
+and the characters \textnl{r} and \textnl{s} are important in Chinese
+and Spanish, respectively, for reasons that are unclear to
+us. Similarly, the word \textnl{then} is dominant in the texts of
+Hindi speakers. Finally, it is clear that authors refer to their
+native cultures (and, consequently, native languages and countries);
+the strings \textnl{Turkish}, \textnl{Korea}, and \textnl{Ita} were
+dominant in the texts of Turkish, Korean and Italian native speakers,
+respectively.
 

### 2013-04-07 paper/paper.tex
features

@@
   features approximating the content.
-\item[Misspelling features] Clearly, the spelling errors that learners
-  make in English depend on the phonological properties of their
-  L1. \sw{???}
+\item[Misspelling features] Learning to perceive, produce, and encode non-native phonemic contrasts is extremely difficult for L2 learners \citep{hayes-harb:2008}.
+Since English's orthography is largely phonemic---even if it is irregular in many places, we expect leaners whose native phoneme contrasts are different from those of English to make characteristic spelling errors.
+For example, since Japanese and Korean lack a phonemic /l/-/r/ contrast, we expect native speakers of those languages to be more likely to make spelling errors that confuse {\tt l} and {\tt r} relative to native speakers of languages such as Spanish in which that pair is contrastive.
+To make this information available to our model, we use a noisy channel spelling corrector \citep{kernighan:1990} to identify and correct misspelled words in the training and test data.
+From these corrections, we extract minimal edit features that show what insertions, deletions, substitutions and joinings (where two separate words are written merged into a single orthographic token) were made by the author of the essay.
 \item[Restored tags] We focus on three important token classes defined
@@
   misused (insertions, substitutions). To restore hidden tokens we use
-  the \texttt{hidden-ngram} utility provided in SRILM
+  the \texttt{hidden-ngram} utility provided in SRI's language modeling toolkit
   \citep{stolcke02srilm}.
-\item[Brown clusters] \sw{???}
+\item[Brown clusters] \cite{brown:cl1992} describe an algorithm that induces a hierarchical clustering of a language's vocabulary based on each vocabulary item's tendency to appear in similar left and right contexts in a training corpus.
+While originally developed to reduce the number of parameters required in $n$-gram language models, Brown clusters have been found to be extremely effective as lexical representations in a variety of regression problems that condition on text \citep{koo:2008,turian:acl2010,owoputi:2013}.
+Using an open-source implementation of the algorithm,\footnote{\url{https://github.com/percyliang/brown-cluster}} we clustered 8~billion words of English into 600~classes.\footnote{\url{http://www.ark.cs.cmu.edu/cdyer/en-600/cluster_viewer.html}}  We included log counts of all $4$-grams of Brown clusters that occurred at least $100$ times in the NLI training data.
+
 \end{compactdesc}

### 2013-04-07 analysis/stats.py
corpus stats

@@ -1,0 +1,73 @@
+#!/bin/env python2.7
+
+import sys, collections
+from os import listdir
+from os.path import isfile, join
+
+class Stats:
+  def __init__(self):
+    self.num_essays = 0
+    self.num_sentences = 0
+    self.num_tokens = 0
+    self.all_types = set()
+
+  def AddFileStats(self, f):
+    self.num_essays += 1
+    for s in f:
+      sentence = s.strip().split()
+      if len(sentence) > 0:
+        self.num_sentences += 1
+        self.num_tokens += len(sentence)
+        for word in sentence:
+          word = word.lower()
+          if not word in self.all_types:
+            self.all_types.add(word)
+
+  def __repr__(self):
+    return "Total essays\t%d\nAvg. sentences per essay\t%.2f\nAvg. tokens per essay\t%.2f\nTotal tokens\t%d\nTotal types\t%d"%(self.num_essays, self.num_sentences/float(self.num_essays), self.num_tokens/float(self.num_essays), self.num_tokens, len(self.all_types))
+
+def PrintStats(essays, metadata, item_in_metadata):
+  # item_in_metadata 0-language, 1-prompt, 2-level 
+  result = collections.defaultdict(Stats)
+  for filename, essay in essays.iteritems():
+    all_items = metadata[filename]
+    item = all_items[item_in_metadata]
+    essay = essays[filename]
+    result[item].AddFileStats(essay)
+
+  for item, stats in result.iteritems():
+    print item
+    print stats
+       
+def ReadCorpusMetadata(metadata_filename):
+  metadata = {}
+  for line in metadata_filename:
+    filename, prompt, language, level = line.strip().split(",")
+    metadata[filename] = (language, prompt, level)
+  return metadata
+
+def CollectData(in_dir):
+  files = {}
+  filenames = [ f for f in listdir(in_dir) if isfile(join(in_dir,f)) ]
+  for f in filenames:
+    files[f] = open(join(in_dir,f)).read().split('\n')
+  return files
+
+
+def main(args):
+  usage = './stats.py in_dir metadata_file'
+  if len(args) < len(usage.split()) - 1:
+    print 'usage:', usage
+    sys.exit(1)
+
+  essays = CollectData(args[1])
+  metadata = ReadCorpusMetadata(open(args[2]))
+  PrintStats(essays, metadata, 0)
+  PrintStats(essays, metadata, 1)
+  PrintStats(essays, metadata, 2)
+
+
+if __name__ == '__main__':
+  main(sys.argv)
+
+

### 2013-04-07 paper/paper.tex
brown, creg

@@
 
+For classification we use the {\tt creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
+\begin{align*}
+p(y& \mid \textbf{w}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{w}, i) ,
+\end{align*}
+where $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}
+
 All essays were tagged with the Stanford part-of-speech tagger
@@
 \item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
-  to count every POS 1-, 2-, and 3-gram in each
-  document. 53.92\%. \sw{But the table says 55.18}
+  to count every POS 1-, 2-, 3- and 4-gram in each
+  document. 55.18\%. 
 \item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
@@
   features defined above with the prompt ID. 65.09\%.
-\item[\feat{Brown}] Brown clusters. \sw{???}
+\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document. 72.26\%.
 \end{compactdesc}
@@
 features listed in \Tref{tbl:addfeats}. Using all these features, the
-accuracy on the development set is \sw{???}, and on the test set it
+accuracy on the development set is~84.55\%, and on the test set it
 is~81.5\%. \Tref{tbl:matrix} lists the confusion matrix on the test

### 2013-04-08 paper/paper.tex
w->d

@@
 \begin{align*}
-p(y& \mid \textbf{w}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{w}, i) ,
+p(y& \mid \textbf{d}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{d}, i) ,
 \end{align*}
-where $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}
+where $\textbf{d}$ are documents, $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}
 

### 2013-04-08 paper/paper.tex
discussion from Noam

@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Discussion}
+\label{sec:discussion}
+
+\nt{We experimented with different classifiers and a large set of features to solve an 11-way classification problem.
+Most of our features are linguistically informed and we believe that this direction should be further pursued.
+Potentially there are at least three motivations for identifying the mother tongue of L1 learners: (1) for the sake of sports, in which case linguistic and pedagogical theory doesn't matter: the more accurate the better; (2) to facilitate human assessment and grading; (3) to point out the differences between different L2 writers, on the one hand, and to discriminate L2 writers as a single set from native tongue writers, on the other; this can pave the way for improving teaching methods and identify the individual difficulties of specific L1 learners.}
+
+\nt{Our point of departure was the analogy between translated texts as a genre in its own and L2 writers as pseudo translators, relying heavily on their mother tongue and transferring their native models to a second language.
+Moreover, we assumed that like translators, L2 writers will write in a simplified manner and overuse explicit markers.
+Although this should be studied vis-a-vis comparable outputs of mother tongue writers in English, we observe that the best features in our classifier are of the ``interference'' type, i.e.
+phonological, morphological and syntactic, mostly in the form of misspelling features, restoration tags, punctuation and lexical and syntactic modeling.
+}
+
+\nt{We would like to stress that certain features indicating L2 do not have any bearing on the quality of the English produced, a phenomenon discussed extensively in Translation Studies \cite{Toury:1995}), were interference is observed by the over- or underuse of certain features.
+reflecting the typological differences between a specific pair of languages.
+For example, the fact that Italian native speakers favor the syntactic sequence of determiner + adjective + noun (e.g., ``a big risk'' or ``this new business'') has zero prescriptive value for teachers.}
+
+\nt{Last, we noted that certain L2 writers tend to repeat more often words appearing in the prompts, i.e.
+in the questions that triggered their essays.
+When we experimented on certain classifiers with and without the prompt number as a feature, we actually noted a decrease in performance.
+For the sake of sports, we should have in fact removed them from our classifier, but we stress their theoretical importance: some L2 writers repeat them more often and this may reflect different educational background (introducing this as a feature offsets its effect).
+Had we had a hypothetical 12th unseen L2, we believe it would have enabled us to cross-classify better.
+Again, this feature says nothing about the quality of the text, just as the tendency of Korean and Italian writers to mention their home country more often does not.
+}
+%\section{Conclusion}
+%\label{sec:conclusion}
 

### 2013-04-08 paper/paper.tex
dataset

@@
 \label{sec:methodology}
-Characteristics of the dataset. Development, train, test sets.
+Training and development set released by the NLI Shared task \citep{tetreault-EtAl:2012:PAPERS} is a balanced set of 1000 TOEFL essays per L1,  10 to 20 sentences each, 900 documents for training and 100 for development.
+Each document is annotated with a writers English proficiency level (low, medium, high) and a prompt (1 to 8).
+All essays are tokenized and split to sentences.
+We detail in  \Tref{tbl:stats:level} training corpora statistics split by writers proficiency.
 
-For classification we use \emph{creg}... \nss{Here we can talk about
-  learning and regularization and give a high-level overview of
-  features.}
+\begin{table}[hbt]
+\small\centering
+\begin{tabular}{lrcc}
+% \textbf{Proficiency}  & \textbf{\# Documents} & \textbf{\# Tokens} & \textbf{\# Types} \\
+%\hline
+%Low & 1.069 & 245,130 & 13,110 \\
+%Medium & 5,366 & 1,819,407 & 37,393 \\ 
+%High & 3,456 & 1,388,260 & 28,329 \\ 
+  & \textbf{Low} & \textbf{Medium} & \textbf{High} \\
+\hline
+\# Documents & 1,069 & 5,366 & 3,456 \\
+\# Tokens & 245,130 & 1,819,407 & 1,388,260 \\ 
+\# Types & 13,110 & 37,393 & 28,329 \\ 
+\end{tabular}
+\caption{Training set statistics.}
+\label{tbl:stats:level}
+\end{table}
 
@@
   to include only those character $n$-grams that are observed more
-  than $m$ times in the corpus are considered. \sw{$n$ ranges from~1
-    to~4, and $m$ is set to~???. 74.12\%}
+  than $m$ times in the corpus are considered. $n$ ranges from~1
+    to~4, and $m$ is set to~5. 74.12\%
 \item[\feat{CharPrompt}] Conjunction of the character $n$-gram
@@
 
-\nt{We would like to stress that certain features indicating L2 do not have any bearing on the quality of the English produced, a phenomenon discussed extensively in Translation Studies \cite{Toury:1995}), were interference is observed by the over- or underuse of certain features.
+\nt{We would like to stress that certain features indicating L2 do not have any bearing on the quality of the English produced, a phenomenon discussed extensively in Translation Studies \citep{Toury:1995}), were interference is observed by the over- or underuse of certain features.
 reflecting the typological differences between a specific pair of languages.

### 2013-04-08 paper/paper.tex
commit

--- 2013-04-08 paper/paper.tex
@@
 \label{sec:methodology}
-Characteristics of the dataset. Development, train, test sets.
+The dataset released by the NLI Shared task \citep{tetreault-EtAl:2012:PAPERS} is a balanced set of 1000 TOEFL essays per each native language.
+Essays are short, consisting of 10 to 20 sentences each.
+The dataset is split into 900 documents for training and 100 for development.
+Each document is annotated with the author's English proficiency level (low, medium, high) and an identification (1 to 8) of the prompt given to the author to trigger the essay.
+All essays are tokenized and split into sentences.
+We detail in \Tref{tbl:stats:level} some statistics on the training corpora, listed by the authors' proficiency level.
 
-For classification we use \emph{creg}... \nss{Here we can talk about
-  learning and regularization and give a high-level overview of
-  features.}
+\begin{table}[hbt]
+\small\centering
+\begin{tabular}{lrrr}
+% \textbf{Proficiency}  & \textbf{\# Documents} & \textbf{\# Tokens} & \textbf{\# Types} \\
+%\hline
+%Low & 1.069 & 245,130 & 13,110 \\
+%Medium & 5,366 & 1,819,407 & 37,393 \\ 
+%High & 3,456 & 1,388,260 & 28,329 \\ 
+  & \multicolumn{1}{c}{\textbf{Low}} & \multicolumn{1}{c}{\textbf{Medium}} & \multicolumn{1}{c}{\textbf{High}} \\
+\hline
+\# Documents & 1,069 & 5,366 & 3,456 \\
+\# Tokens & 245,130 & 1,819,407 & 1,388,260 \\ 
+\# Types & 13,110 & 37,393 & 28,329 \\ 
+\end{tabular}
+\caption{Training set statistics.}
+\label{tbl:stats:level}
+\end{table}
 
-For classification we use the {\tt creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
+For classification we use the \texttt{creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
 \begin{align*}
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Discussion}
+\label{sec:discussion}
+
+We experimented with different classifiers and a large set of features to solve an 11-way classification problem.
+Most of our features are linguistically informed and we believe that this direction should be further pursued.
+There are at least three motivations for identifying the mother tongue of L1 learners: (1) for the sake of sports, in which case linguistic and pedagogical theory doesn't matter: the more accurate the better; (2) to facilitate human assessment and grading; (3) to point out the differences between different L2 writers, on the one hand, and to discriminate L2 writers as a single set from native tongue writers, on the other; this can pave the way for improving teaching methods and identify the individual difficulties of specific L1 learners.
+
+Our point of departure was the analogy between translated texts as a genre in its own and L2 writers as pseudo translators, relying heavily on their mother tongue and transferring their native models to a second language.
+Moreover, we assumed that like translators, L2 writers will write in a simplified manner and overuse explicit markers.
+Although this should be studied vis-a-vis comparable outputs of mother tongue writers in English, we observe that the best features of our classifiers are of the ``interference'' type, i.e.
+phonological, morphological and syntactic in nature, mostly in the form of misspelling features, restoration tags, punctuation and lexical and syntactic modeling.
+
+We would like to stress that certain features indicating L2 do not have any bearing on the quality of the English produced, a phenomenon discussed extensively in Translation Studies \citep{Toury:1995}, where interference is observed by the overuse or underuse of certain features reflecting the typological differences between a specific pair of languages.
+For example, the fact that Italian native speakers favor the syntactic sequence of determiner + adjective + noun (e.g., \textnl{a big risk} or \textnl{this new business}) has little prescriptive value for teachers.
+
+Last, we noted that certain L2 writers tend to repeat more often words appearing in the prompts, i.e., in the questions that triggered their essays.
+When we experimented on certain classifiers with and without the prompt number as a feature, we actually noted a decrease in performance.
+For the sake of sports, we should have in fact removed them from our classifier, but we stress their theoretical importance: some L2 writers repeat them more often and this may reflect different educational backgrounds (introducing this as a feature offsets its effect).
+Had we had a hypothetical 12th unseen L2, we believe it would have enabled us to cross-classify better.
+Again, this feature says nothing about the quality of the text, just as the tendency of Korean and Italian writers to mention their home country more often does not.
+%\section{Conclusion}
+%\label{sec:conclusion}
 

### 2013-04-08 paper/paper.tex
examples

@@
   to count every POS 1-, 2-, 3- and 4-gram in each
-  document. 55.18\%. 
+  document. 55.18\%. \yt{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
 \item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
@@
   than $m$ times in the corpus are considered. $n$ ranges from~1
-    to~4, and $m$ is set to~5. 74.12\%
+    to~4, and $m$ is set to~5. 74.12\% \yt{TUR:T u r k, ITA:I t a l, JPN:J a p a, \textbf{ITA: o v e} :) }  
 \item[\feat{CharPrompt}] Conjunction of the character $n$-gram
   features defined above with the prompt ID. 65.09\%.
-\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document. 72.26\%.
+\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document.
+72.26\%.
+\yt{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)}
 \end{compactdesc}
@@
   for the first two and last three words before the period in each
-  sentence as features. 53.03\%.
+  sentence as features. 53.03\%. \yt{ARA: second word `,', CHI: second word `is', HIN: second word `can'}  
 \item[\feat{PsvRatio}] The proportion of passive verbs out of all
@@
 \item[\feat{CxtFxn}] Contextual function words. Bi-grams yield
-  62.79\%, tri-gram 62.32\%.
-\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%.
+  62.79\%, tri-gram 62.32\%. \yt{CHI: some JJ, HIN: as VBN, } 
+\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%. \yt{ARA: DEL:e, INS:e, SUBST:e:i; GER: SUBST:z:y; JPN: SUBST:l:r, SUBST:r:l;SPA: DOUBLE:s, MID:INS:s, INS:s }
 \item[\feat{Restore}] Counts of substitutions, deletions and
-  insertions of predefined tokens that we restored in the texts. 47.67\%
+  insertions of predefined tokens that we restored in the texts. 47.67\% \yt{CHI: Delete do, GER: Delete on, ITA Delete be}  
 \end{compactdesc}

### 2013-04-09 paper/paper.tex
abstract

@@
 \begin{abstract}
-Given a dataset of English essays composed by non-native speakers, as
-part of the TOEFL exam, we identify with high accuracy the native
-language of the authors. We use standard text classification
-techniques, but define sophisticated classifiers that are sensitive to
-the specific patterns observed in the English of authors whose first
-language is structurally different. We describe the various features
+We show that it is possible to learn to identify, with high accuracy, the native language of English test takers writers from the content of the essays they write.
+Our method uses standard text classification
+techniques based on multiclass logistic regression to exploit in conjunction individually weak indicators to predict the most probable native language from a set of 11 possibilities.
+We describe the various features
 used for classification, as well as the settings of the classifier

### 2013-04-09 paper/paper.tex
features example

@@
 \newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
+\newcommand{\featstr}[1]{\textsmaller[.5]{\verb|#1|}} % full feature name
 \newcommand{\textnl}{\textsl}
@@
 features used to identify translationese by \citet{vered:noam:shuly}.
-We begin by motivating our choice of features.
+We begin by motivating our choice of features, many of which are illustrated in \fref{fig:german} for an example sentence.
+
+\begin{figure*}\centering\small
+Firstly the employers live more savely because they are going to have more money to spend for luxury .\\[10pt]
+
+\begin{tabular}{p{6em}p{15em}p{15em}}
+ & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
+\hline
+\bf Characters & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"CHAR_l_y_ "|:&$\log{2+1}$\\ \verb|"CharPrompt_P5_g_o_i"|:&$\log{1+1}$\\ \verb|"MFChar_e_ "|:&$\log{1+1}$\\ \verb|"Punc_period"|:&$\log{1+1}$\end{tabular}
+ & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"DeleteP_p_."|:&$1.0$\\ \verb|"InsertP_p_,"|:&$1.0$\\ \verb|"MID:SUBST:v:f"|:&$\log{1+1}$\\ \verb|"SUBST:v:f"|:&$\log{1+1}$\end{tabular} \\
+\hline
+\bf Words & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"DocLen_"|:&$\log{19+1}$\\ \verb|"MeanWordRank"|:&$422.6$\\ \verb|"CohMarker_because"|:&$\log{1+1}$\\ \verb|"MostFreq_have"|:&$\log{1+1}$\\
+\verb|"PosToken_last_luxury"|:&$\log{1+1}$\\ \verb|"Pronouns_they"|:&$\log{1+1}$\end{tabular}
+ & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"MSP:safely"|:&$\log{1+1}$\\ \verb|"Match_p_to"|:&$0.5$\\ \verb|"Delete_p_to"|:&$0.5$\\ \verb|"Delete_p_are"|:&$1.0$\\ \verb|"Delete_p_because"|:&$1.0$\\
+\verb|"Delete_p_for"|:&$1.0$\end{tabular} \\
+\hline
+\bf POS & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"POS_VBP_VBG_TO"|:&$\log{1+1}$\\ \verb|"POS_p_VBP_VBG_TO"|:&$0.059$\end{tabular} \\
+\hline
+\bf Words + POS & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"VBP_VBG_to"|:&$\log{1+1}$\\ \verb|"FW__more RB"|:&$\log{1+1}$\end{tabular} \\
+\hline
+\end{tabular}
+
+\caption{Some of the features extracted for an L1 German sentence.}\label{fig:german}
+\end{figure*}
 
@@
 First, we use the following four feature types as the core of our
-model.  Whenever counts are mentioned, we use the log of the count as
+model.  Whenever counts are mentioned, we use the log of the count-plus-one\nss{added: plus one} as
 the feature.  We report the accuracy of using each feature type, in

### 2013-04-09 paper/paper.tex
lbfgs few fixes

@@
 \title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
-{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
+{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Victor Chahuneau$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
 }
@@
 The task we address in this work is identifying the native language
-(\emph{L1}) of non-native English (\emph{L2}) authors. More specifically, given a
+(L1) of non-native English (L2) authors. More specifically, given a
 dataset of short English essays
@@
 
-We address the task as a multiway text-classification task; we specify
-our methodology in \Sref{sec:methodology}. As in other author
+We address the task as a multiway text-classification task; we describe our data in \Sref{sec:data} and classification model in \Sref{sec:model}. As in other author
 attribution tasks \citep{joula:2006}, the choice of features for the
@@
 International Corpus of Learner English \citep{icle}, which includes
-texts written by students from Russia, the Czech Republic, Bulgaria,
-France, and Spain. The texts lengths range from 500 to 850 words. The
-classification method is a linear SVM, and features include 400
-standard function words, 200 letter $n$-grams, 185 error types and 250
+texts written by students from 5 countries, Russia, the Czech Republic, Bulgaria,
+France, and Spain. The texts lengths range from 500~to 850~words. Their
+classification method is a linear SVM, and features include 400~standard function words, 200~letter $n$-grams, 185~error types and 250
 rare part-of-speech (POS) bi-grams. Ten-fold cross-validation results
@@
 
-\section{Methodology}
-\label{sec:methodology}
+\section{Data}
+\label{sec:data}
 The dataset released by the NLI Shared task \citep{tetreault-EtAl:2012:PAPERS} is a balanced set of 1000 TOEFL essays per each native language.
@@
 We detail in \Tref{tbl:stats:level} some statistics on the training corpora, listed by the authors' proficiency level.
+All essays were tagged with the Stanford part-of-speech tagger
+\citep{toutanova-03}. We did not parse the dataset.
 
@@
 
-For classification we use the \texttt{creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
+\section{Model}
+\label{sec:model}
+For our classification model we used the \texttt{creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the classifier as a multiclass logistic regression:
 \begin{align*}
-p(y& \mid \textbf{d}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{d}, i) ,
+p_{\boldsymbol{\lambda}}(y& \mid \textbf{x})= \frac{\exp \sum_j \lambda_j h_j(y, \textbf{x})}{Z_{\boldsymbol{\lambda}}(\textbf{x})} ,
 \end{align*}
-where $\textbf{d}$ are documents, $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}
+where $\textbf{x}$ are documents, $h_j(\cdot)$ are real-valued feature functions, $\lambda_j$ are the corresponding weights, and $y$ is one of the eleven L1 class labels.
+To train the parameters of our model, we minimized the following objective,
+\begin{align*}
+\mathcal{L} = \alpha \overbrace{\sum_j \lambda_j^2}^{\textrm{$\ell_2$ reg.}} - \sum_{\{(\textbf{x}_i,y_i )\}_{i=1}^{|\mathcal{D}|}} \Big(& \overbrace{\log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}^{\textrm{log likelihood}}  + \\
+& \tau \underbrace{\mathbb{E}_{p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)} \log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}_{-\textrm{conditional entropy}}\Big) ,
+\end{align*}
+which combines the negative log likelihood of the training dataset $\mathcal{D}$, an $\ell_2$ (quadratic) penalty on the magnitude of $\boldsymbol{\lambda}$ (weighted by $\alpha$), and the \emph{negative} entropy of the predictive model (weighted by $\tau$).
+While an $\ell_2$ weight penalty is standard in regression problems like this, we found that the the additional entropy term gave more reliable results.
+Intuitively, the entropic regularizer encourages the remain maximally uncertain about its predictions.
+In the metaphor of ``maximum entropy'', the entropic prior finds a solution that has \emph{more} entropy than the ``maximum'' model that is compatible with the constraints.
 
-All essays were tagged with the Stanford part-of-speech tagger
-\citep{toutanova-03}. We did not parse the dataset.
+The objective cannot be minimized in closed form, but it does have a unique minimum and is straightforwardly differentiable, so we used L-BFGS to find the optimal weight settings \citep{lbfgs}.
 
-\section{Model Overview}
+\section{Feature Overview}
 \label{sec:features}

### 2013-04-09 paper/paper.tex
moar

@@
   (TOEFL)} by authors whose native language is one out of~11 possible
-languages (Arabic, Chinese, French, German, Hindi, Italian, Japanese,
-Korean, Spanish, Telugu, and Turkish), our task is to identify that
+languages---Arabic, Chinese, French, German, Hindi, Italian, Japanese,
+Korean, Spanish, Telugu, or Turkish---our task is to identify that
 language.
@@
 different errors when they write English, depending on their native
-language \citep{swan2001learner}; understanding the different types of
+language \citep{lado-57,swan2001learner}; understanding the different types of
 errors is a prerequisite for correcting them
@@
 to the task can be linguistically interpreted.
+Briefly, our features draw heavily on prior work in general text classification and authorship identification, those used in identifying so-called \emph{translationese} \cite{vered:noam:shuly}, and a class of features that involves  determining what minimal changes would be necessary to transform the essays into ``standard'' English (as determined by an $n$-gram language model).
 
@@
 texts written by students from 5 countries, Russia, the Czech Republic, Bulgaria,
-France, and Spain. The texts lengths range from 500~to 850~words. Their
+France, and Spain. The texts range from 500~to 850~words in length. Their
 classification method is a linear SVM, and features include 400~standard function words, 200~letter $n$-grams, 185~error types and 250
-rare part-of-speech (POS) bi-grams. Ten-fold cross-validation results
+rare part-of-speech (POS) bigrams. Ten-fold cross-validation results
 on this dataset are 80\% accuracy.
@@
 in testing the hypothesis that an author's choice of words in a second
-language is influenced by the phonology of his or her L1. They confirm
+language is influenced by the \emph{phonology} of his or her L1. They confirm
 this hypothesis by carefully analyzing the features used by
@@
 \citet{Wong-Dras:2009:ALTA2009,wong-dras:2011:EMNLP} are also
-motivated by a linguistic hypothesis, namely that syntactic errors in
+motivated by a linguistic hypothesis, namely that \emph{syntactic} errors in
 a text are influenced by the author's
@@
 Swiss German, Dutch, Swedish and Danish) and five Romance languages
-(French, Italian, Catalan, Spanish and Portuguese). Again, SVM is the
+(French, Italian, Catalan, Spanish and Portuguese). Again, SVMs are used as the
 classification device. Features include POS $n$-grams, character
@@
 \citet{brooke2011native}. Since training corpora for this task are
-rare, they use mainly L1 (blog) corpora. Given English word bi-grams
+rare, they use mainly L1 (blog) corpora. Given English word bigrams
 $\langle e_1,e_2\rangle$, they try to assess, for each L1, how likely
@@
 Spanish, Chinese, and Japanese), and evaluating on the International
-Corpus of Learner English, the results are lower than 50\%.
-
-Our dataset in this work is different, and consists of TOEFL essays
-written by speakers of eleven different L1s
-\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR},
-distributed as part of the First Native Language Identification Shared
-Task \citep{tetreault-blanchard-cahill:2013:BEA}. We use a plethora of
-features; some of them are inspired by previous work outlined above,
-but many are motivated by other author attribution tasks, in
-particular identification of \emph{translationese}, the language of
-translated texts \citep{vered:noam:shuly}.
+Corpus of Learner English, accuracy is below 50\%.
 
@@
 \label{sec:data}
-The dataset released by the NLI Shared task \citep{tetreault-EtAl:2012:PAPERS} is a balanced set of 1000 TOEFL essays per each native language.
-Essays are short, consisting of 10 to 20 sentences each.
-The dataset is split into 900 documents for training and 100 for development.
-Each document is annotated with the author's English proficiency level (low, medium, high) and an identification (1 to 8) of the prompt given to the author to trigger the essay.
+Our dataset in this work consists of TOEFL essays
+written by speakers of eleven different L1s
+\citep{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR},
+distributed as part of the Native Language Identification Shared
+Task \citep{tetreault-blanchard-cahill:2013:BEA}.
+The training data consists of 1000 essays from each native language.
+The essays are short, consisting of 10~to 20~sentences each.
+We used the provided splits of 900 documents for training and 100 for development.
+Each document is annotated with the author's English proficiency level (low, medium, high) and an identification (1 to 8) of the essay prompt.
 All essays are tokenized and split into sentences.
-We detail in \Tref{tbl:stats:level} some statistics on the training corpora, listed by the authors' proficiency level.
+In \Tref{tbl:stats:level} we provide some statistics on the training corpora, listed by the authors' proficiency level.
 All essays were tagged with the Stanford part-of-speech tagger
@@
 \begin{align*}
-p_{\boldsymbol{\lambda}}(y& \mid \textbf{x})= \frac{\exp \sum_j \lambda_j h_j(y, \textbf{x})}{Z_{\boldsymbol{\lambda}}(\textbf{x})} ,
+p_{\boldsymbol{\lambda}}(y& \mid \textbf{x})= \frac{\exp \sum_j \lambda_j h_j(\textbf{x},y)}{Z_{\boldsymbol{\lambda}}(\textbf{x})} ,
 \end{align*}
-where $\textbf{x}$ are documents, $h_j(\cdot)$ are real-valued feature functions, $\lambda_j$ are the corresponding weights, and $y$ is one of the eleven L1 class labels.
+where $\textbf{x}$ are documents, $h_j(\cdot)$ are real-valued feature functions of the document being classified, $\lambda_j$ are the corresponding weights, and $y$ is one of the eleven L1 class labels.
 To train the parameters of our model, we minimized the following objective,
@@
 \mathcal{L} = \alpha \overbrace{\sum_j \lambda_j^2}^{\textrm{$\ell_2$ reg.}} - \sum_{\{(\textbf{x}_i,y_i )\}_{i=1}^{|\mathcal{D}|}} \Big(& \overbrace{\log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}^{\textrm{log likelihood}}  + \\
-& \tau \underbrace{\mathbb{E}_{p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)} \log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}_{-\textrm{conditional entropy}}\Big) ,
+& \tau \underbrace{\mathbb{E}_{p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)} \log p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)}_{-\textrm{conditional entropy}}\Big) ,
 \end{align*}
@@
 
-\subsection{Motivation}
-While some of the features were used in the works surveyed in
-\Sref{sec:literature}, many are novel, and are inspired by the
-features used to identify translationese by \citet{vered:noam:shuly}.
-We begin by motivating our choice of features, many of which are illustrated in \fref{fig:german} for an example sentence.
+While some of the features were used in prior work (\Sref{sec:literature}), we focus on two broad novel categories of features: those inspired by the
+features used to identify translationese by \citet{vered:noam:shuly} and those extracted by automatic statistical ``correction'' of the essays.
+Refer to \fref{fig:german} to see the set of features and their values that were extracted from an example sentence.
 
@@
 
-\subsection{Main Features}
+\subsection{Primary Features}
 \label{sec:mainfeats}
-First, we use the following four feature types as the core of our
-model.  Whenever counts are mentioned, we use the log of the count-plus-one\nss{added: plus one} as
-the feature.  We report the accuracy of using each feature type, in
-isolation, on the training set.
+First, we use the following four feature types as the baseline features in our
+model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
+the feature's value.  For each feature type, we report the accuracy of using just that feature type in
+isolation on the training set\cjd{training? development? cross validated?}.
 

### 2013-04-09 paper/paper.tex
moar

@@
 %\newcommand{\arkcomment}[3]{}
+\newcommand{\ignore}[1]{}
 \newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
@@
 
-\subsection{Primary Features}
+\subsection{Main Features}
 \label{sec:mainfeats}
-First, we use the following four feature types as the baseline features in our
+FWe use the following four feature types as the baseline features in our
 model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
 the feature's value.  For each feature type, we report the accuracy of using just that feature type in
-isolation on the training set\cjd{training? development? cross validated?}.
+isolation on the training set\cjd{training? development? cross validated?} in Tab.~\ref{tbl:mainfeats}.
 
@@
   to count every POS 1-, 2-, 3- and 4-gram in each
-  document. 55.18\%. \yt{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
+  document. 55.18\%. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
 \item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
-  with character $n$-grams: The number of character 1-, 2-, and
-  3-grams. This yielded 69.94\% accuracy.  We then refined the feature
-  to include only those character $n$-grams that are observed more
-  than $m$ times in the corpus are considered. $n$ ranges from~1
-    to~4, and $m$ is set to~5. 74.12\% \yt{TUR:T u r k, ITA:I t a l, JPN:J a p a, \textbf{ITA: o v e} :) }  
-\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
-  features defined above with the prompt ID. 65.09\%.
-\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document.
-72.26\%.
-\yt{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)}
+  with character $n$-grams: To reduce the number of parameters, we removed features
+  only those character $n$-grams that are observed more
+  than $5$ times in the training corpus, and $n$ ranges from~1
+    to~4. Accuracy: $74.12\%$. High-weight features include: {\tt TUR:Turk}, {\tt ITA:Ital}, {\tt JPN:Japa}.\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
+  features defined above with the prompt ID. Accuracy: 65.09\%.
+\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster unigrams and bigrams in each document.
+Accuracy: 72.26\%.
+\ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)}
 \end{compactdesc}

### 2013-04-09 paper/paper.tex
per-feature accuracies

@@
 All essays are tokenized and split into sentences.
-In \Tref{tbl:stats:level} we provide some statistics on the training corpora, listed by the authors' proficiency level.
+In \tref{tbl:stats:level} we provide some statistics on the training corpora, listed by the authors' proficiency level.
 All essays were tagged with the Stanford part-of-speech tagger
@@
 
+\begin{table}\centering\small
+\begin{tabular}{l@{}c}
+\bf Feature & \bf Accuracy (\%) \\
+\hline
+\feat{POS} & 55.18\\
+\feat{FreqChar} & 74.12\\
+\feat{CharPrompt} & 65.09\\
+\feat{Brown} & 72.26\\
+\hline
+\feat{DocLen} & 11.81\\
+\feat{Punct} & 27.41\\
+\feat{Pron} & 22.81\\
+\feat{Position} & 53.03\\
+\feat{PsvRatio} & 12.26\\
+\feat{CxtFxn} \textsmaller{(bigram)} & 62.79\\
+\feat{CxtFxn} \textsmaller{(trigram)} & 62.32\\
+\feat{Misspell} & 37.29\\
+\feat{Restore} & 47.67\\ 
+\hline
+\feat{CohMark} & 25.71\\
+\feat{CohVerb} & 22.85\\
+\feat{FxnWord} & 42.47\\
+\hline
+\end{tabular}
+\caption{Independent performance of feature types detailed in \Sref{sec:mainfeats}, \Sref{sec:addfeats} and \Sref{sec:discarded}. 
+Accuracy is averaged over 10 folds of cross-validation on the training set.}
+\end{table}
+
 \subsection{Main Features}
@@
 model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
-the feature's value.  For each feature type, we report the accuracy of using just that feature type in
-isolation on the training set\cjd{training? development? cross validated?} in Tab.~\ref{tbl:mainfeats}.
+the feature's value.  \Tref{tbl:mainfeats} reports the accuracy of using each feature type in
+isolation (with 10-fold cross-validation on the training set).
 
@@
   to count every POS 1-, 2-, 3- and 4-gram in each
-  document. 55.18\%. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
+  document. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
 \item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
@@
   than $5$ times in the training corpus, and $n$ ranges from~1
-    to~4. Accuracy: $74.12\%$. High-weight features include: {\tt TUR:Turk}, {\tt ITA:Ital}, {\tt JPN:Japa}.\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
-  features defined above with the prompt ID. Accuracy: 65.09\%.
-\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster unigrams and bigrams in each document.
-Accuracy: 72.26\%.
-\ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)}
+    to~4. High-weight features include: {\tt TUR:Turk}, {\tt ITA:Ital}, {\tt JPN:Japa}.
+\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
+  features defined above with the prompt ID.
+\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster 
+unigrams and bigrams in each document.\ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)} 
 \end{compactdesc}
@@
 The accuracy of the classifier on the development set using these four
-feature types is reported in \Tref{tbl:mainfeats}.
+feature types is reported in \tref{tbl:mainfeats}.
 
@@
 
-\subsection{Additional Features}
+\subsection{Additional Features}\label{sec:addfeats}
 To the basic set of features we now add more specific,
@@
 \begin{compactdesc}
-\item[\feat{DocLen}] Document length in tokens. 11.81\%.
-\item[\feat{Punct}] Counts of each punctuation mark. 27.41\%. 
-\item[\feat{Pron}] Counts of each pronoun. 22.81\%.
+\item[\feat{DocLen}] Document length in tokens.
+\item[\feat{Punct}] Counts of each punctuation mark. 
+\item[\feat{Pron}] Counts of each pronoun.
 \item[\feat{Position}] Positional token frequency. We use the counts
   for the first two and last three words before the period in each
-  sentence as features. 53.03\%. \yt{ARA: second word `,', CHI: second word `is', HIN: second word `can'}  
+  sentence as features. \yt{ARA: second word `,', CHI: second word `is', HIN: second word `can'}  
 \item[\feat{PsvRatio}] The proportion of passive verbs out of all
-  verbs. 12.26\%.
-\item[\feat{CxtFxn}] Contextual function words. Bi-grams yield
-  62.79\%, tri-gram 62.32\%. \yt{CHI: some JJ, HIN: as VBN, } 
-\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%. \yt{ARA: DEL:e, INS:e, SUBST:e:i; GER: SUBST:z:y; JPN: SUBST:l:r, SUBST:r:l;SPA: DOUBLE:s, MID:INS:s, INS:s }
+  verbs.
+\item[\feat{CxtFxn}] Contextual function words. \yt{CHI: some JJ, HIN: as VBN, } 
+\item[\feat{Misspell}] Spelling correction edits. \sw{???}. \yt{ARA: DEL:e, INS:e, SUBST:e:i; GER: SUBST:z:y; JPN: SUBST:l:r, SUBST:r:l;SPA: DOUBLE:s, MID:INS:s, INS:s }
 \item[\feat{Restore}] Counts of substitutions, deletions and
-  insertions of predefined tokens that we restored in the texts. 47.67\% \yt{CHI: Delete do, GER: Delete on, ITA Delete be}  
+  insertions of predefined tokens that we restored in the texts. \yt{CHI: Delete do, GER: Delete on, ITA Delete be}  
 \end{compactdesc}
@@
 \caption{Dev set accuracy with \textsc{main} features plus additional feature groups, added independently. 
-$\ell_2$ regularization was tuned as in \Tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
+$\ell_2$ regularization was tuned as in \tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
 configuration; more careful tuning might produce slightly better accuracy).
@@
 
-\subsection{Discarded Features}
+\subsection{Discarded Features}\label{sec:discarded}
 We also tried several other feature types that did not improve the
@@
 \begin{compactdesc}
-\item[Cohesive markers] Counts of each cohesive marker. 25.71\%.
-\item[Cohesive verbs] Counts of each cohesive verb. 22.85\%.
-\item[Function words] Counts of function words. 42.47\%. This feature
-  is subsumed by the highly discriminative \feat{CxtFxn} feature.
+\item[\feat{CohMark}] Counts of each cohesive marker.
+\item[\feat{CohVerb}] Counts of each cohesive verb.
+\item[\feat{FxnWord}] Counts of function words. These features
+  are subsumed by the highly discriminative \feat{CxtFxn} features.
 \end{compactdesc}
@@
 The full model that we used to classify the test set combines all
-features listed in \Tref{tbl:addfeats}. Using all these features, the
+features listed in \tref{tbl:addfeats}. Using all these features, the
 accuracy on the development set is~84.55\%, and on the test set it

### 2013-04-09 paper/paper.tex
typo
detailed feature descriptions

@@
 \label{sec:mainfeats}
-FWe use the following four feature types as the baseline features in our
+We use the following four feature types as the baseline features in our
 model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
@@
   than $5$ times in the training corpus, and $n$ ranges from~1
-    to~4. High-weight features include: {\tt TUR:Turk}, {\tt ITA:Ital}, {\tt JPN:Japa}.
+    to~4. High-weight features include: {\tt TUR:<Turk>}; {\tt ITA:<Ital>}; {\tt JPN:<Japa>}.
 \item[\feat{CharPrompt}] Conjunction of the character $n$-gram
@@
   for the first two and last three words before the period in each
-  sentence as features. \yt{ARA: second word `,', CHI: second word `is', HIN: second word `can'}  
+  sentence as features. High-weight features for the \emph{second} word include: {\tt ARA:2<,>}; {\tt CHI:2<is>}; {\tt HIN:2<can>}.
 \item[\feat{PsvRatio}] The proportion of passive verbs out of all
   verbs.
-\item[\feat{CxtFxn}] Contextual function words. \yt{CHI: some JJ, HIN: as VBN, } 
-\item[\feat{Misspell}] Spelling correction edits. \sw{???}. \yt{ARA: DEL:e, INS:e, SUBST:e:i; GER: SUBST:z:y; JPN: SUBST:l:r, SUBST:r:l;SPA: DOUBLE:s, MID:INS:s, INS:s }
+\item[\feat{CxtFxn}] Contextual function words. \raggedright High-weight features include: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}. 
+\item[\feat{Misspell}] Spelling correction edits.
+\sw{???}.
+\raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBT<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
 \item[\feat{Restore}] Counts of substitutions, deletions and
-  insertions of predefined tokens that we restored in the texts. \yt{CHI: Delete do, GER: Delete on, ITA Delete be}  
+  insertions of predefined tokens that we restored in the texts. High-weight features include: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}; {\tt ITA:DELWORD<be>}  
 \end{compactdesc}

### 2013-04-09 paper/paper.tex
typo

@@
 \sw{???}.
-\raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBT<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
+\raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
 \item[\feat{Restore}] Counts of substitutions, deletions and

### 2013-04-09 paper/paper.tex
moar

@@
 \begin{abstract}
-We show that it is possible to learn to identify, with high accuracy, the native language of English test takers writers from the content of the essays they write.
+We show that it is possible to learn to identify, with high accuracy, the native language of English test takers from the content of the essays they write.
 Our method uses standard text classification
-techniques based on multiclass logistic regression to exploit in conjunction individually weak indicators to predict the most probable native language from a set of 11 possibilities.
-We describe the various features
+techniques based on multiclass logistic regression, combining individually weak indicators to predict the most probable native language from a set of 11 possibilities. We describe the various features
 used for classification, as well as the settings of the classifier
@@
 \item[\feat{Misspell}] Spelling correction edits.
-\sw{???}.
+Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred.
 \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
@@
 accuracy on the development set is~84.55\%, and on the test set it
-is~81.5\%. \Tref{tbl:matrix} lists the confusion matrix on the test
+is~81.5\%. The values for $\alpha$ and $\tau$ were tuned to optimize development set performance, and found to be $\alpha=5$,$\tau=2$.
+
+\Tref{tbl:matrix} lists the confusion matrix on the test
 set, as well as precision, recall and $F_1$-score for each L1.
-The largest class of errors was predicting Telugu where the correct label 
-was Hindi\nss{or vice versa?}---this happened 18 times.
+The largest error type involved predicting Telugu when the true label 
+was Hindi, which happened 18 times.  This error is unsurprising since many Hindi and Telugu speakers are arguably native speakers of Indian English.
 
@@
 \begin{tabular}{>{\bf}l|r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r|ccc} %from the email sent by the organizers
-	& \bf ARA & \bf CHI & \bf FRE & \bf GER & \bf HIN & \bf ITA & \bf JPN & \bf KOR & \bf SPA & \bf TEL & \bf TUR & \bf Precision (\%) & \bf Recall (\%) & \bf $F_1$ (\%) \\
+\emph{true}$\downarrow$	& \bf ARA & \bf CHI & \bf FRE & \bf GER & \bf HIN & \bf ITA & \bf JPN & \bf KOR & \bf SPA & \bf TEL & \bf TUR & \bf Precision (\%) & \bf Recall (\%) & \bf $F_1$ (\%) \\
 \hline
@@
 \end{tabular}
-\caption{Official test set confusion matrix with the full model. \nss{which direction is predicted vs. gold?}
+\caption{Official test set confusion matrix with the full model. 
 Accuracy is 81.5\%.}
@@
 and \emph{interlanguage} in second language acquisition
-\citep{Selinker1972}.
-
-\citet{vered:noam:shuly} designed 32 classifiers to test the validity
-of the forces acting on translated texts, and found that interference
+\citep{Selinker1972}. \citet{vered:noam:shuly} designed 32 classifiers to test the validity
+of the forces acting on translated texts, and found that features sensitive to interference
 consistently yielded the best performing classifiers. And indeed, in
-this work too, which replicates some of their classifiers, we find
-again that fingerprints of the source language are dominant in the
-makeup of L2 texts.
-
-The main difference, however, between texts translated by
+this work too, we find fingerprints of the source language are dominant in the
+makeup of L2 texts. The main difference, however, between texts translated by
 professionals and the texts we address here, is that more often than
@@
 whereas L2 writers write out of their mother tongue by definition. So
-interference is ever more exaggerated in their case, for example, also
+interference is ever more exaggerated in this case, for example, also
 phonologically \citep{tsur-rappoport:2007:Cognitive-2007}.
 
-We illustrate this with some examples from Arabic native speakers. The
+We explore the effects of interference by analyzing several patterns we observe in the features.
+Our classifier finds that the
 character sequence \textnl{alot} is overrepresented in Arabic L2
@@
 suffix in English. For the same reason, another prominent feature is a
-missing definite article before nouns and adjectives . Additionally,
+missing definite article before nouns and adjectives. Additionally,
 Arabic, being an Abjad language, rarely indicates vowels, and indeed
@@
 /\textipa{I}/ and /\textipa{@}/ into /i/ (at least in Modern Standard
-Arabic), we see that many \textnl{e}-s are indeed substituted for
-\textnl{i}-s in these texts.
+Arabic), we see that many {\tt e}'s are indeed substituted for
+{\tt i}'s in these texts.
 
-German overuses hyphens in two interesting ways. German can
-notoriously use relative clauses freely, and such constructions
-frequently occur between hyphens in the dataset, as in \textnl{any
+We find that essays that contain hyphens are more likely to be from German authors.
+We again find evidence of interference from the native language here.
+First, relative clauses are widely used in German, and we see this pattern in L2 English of L1 German speakers.
+For example, \textnl{any
   given rational being -- let us say Immanual Kant -- we find
-  that}. Another overuse of hyphens stems from compounding, another
-facet of German, for example in \textnl{well-known},
+  that}. Another source of extra hyphens stems from compounding convention. So, for example, we find \textnl{well-known},
 \textnl{community-help}, \textnl{spare-time}, \textnl{football-club},
@@
 English would be more naturally rendered as \textnl{football club}).
-Another unexpected feature of German is a frequent substitution of the
-letter \textnl{y} for \textnl{z} (and vice versa), most probably
-triggered by their switched positions on German keyboards.
+Another unexpected feature of essays by native Germans is a frequent substitution of the
+letter \textnl{y} for \textnl{z} and vice versa. We suspect this owes to their switched positions on German keyboards.
 
-The word \textnl{that} occurs more frequently in the texts of German
-L1 speakers, perhaps because in English it is optional in relative
-clauses whereas in German it is not.  Last, \textnl{often} is
-overused; being a cognate of the German \textnl{oft} it is not
-cognitively expensive to retrieve it. Spanish, on the other hand,
-literally translates \textnl{muchas veces} into \textnl{many times},
-which is similarly overused on the dataset. \sw{any Spanish speaker
-  who could validate this expression?}
+Lexical item frequency also provides clues to the L1 of the essay writers. The word \textnl{that} occurs more frequently in the texts of German
+L1 speakers. We hypothesize that in English it is optional in relative
+clauses whereas in German it is not, so German speakers are less comfortable using the non-obligatory form.  Also, \textnl{often} is
+over represented. We hypothesize that since it is cognate of German \textnl{oft}, it is not
+cognitively expensive to retrieve it. We find \textnl{many times}---a literal translation of \textnl{muchas veces}--- in Spanish essays.
 
-Other informative features include substitutions of \textnl{r}-s and
-\textnl{l}-s in the texts of Japanese authors, for obvious reasons;
-and the characters \textnl{r} and \textnl{s} are important in Chinese
-and Spanish, respectively, for reasons that are unclear to
-us. Similarly, the word \textnl{then} is dominant in the texts of
+Other informative features that reflect L1 features include frequent misspellings involving confusions of {\tt l} and {\tt r} in Japanese essays.
+More mysteriously, the characters \textnl{r} and \textnl{s} are misused in Chinese
+and Spanish, respectively. The word \textnl{then} is dominant in the texts of
 Hindi speakers. Finally, it is clear that authors refer to their
@@
 We experimented with different classifiers and a large set of features to solve an 11-way classification problem.
-Most of our features are linguistically informed and we believe that this direction should be further pursued.
-There are at least three motivations for identifying the mother tongue of L1 learners: (1) for the sake of sports, in which case linguistic and pedagogical theory doesn't matter: the more accurate the better; (2) to facilitate human assessment and grading; (3) to point out the differences between different L2 writers, on the one hand, and to discriminate L2 writers as a single set from native tongue writers, on the other; this can pave the way for improving teaching methods and identify the individual difficulties of specific L1 learners.
+We hope that studying this problem will improve to facilitate human assessment, grading, and teaching of English as a second language.
+While the core features used are sparse and sensitive to lexical and even orthographic features of the writing, many of them are linguistically informed and provide insight into how L1 and L2 interact.
 
 Our point of departure was the analogy between translated texts as a genre in its own and L2 writers as pseudo translators, relying heavily on their mother tongue and transferring their native models to a second language.
-Moreover, we assumed that like translators, L2 writers will write in a simplified manner and overuse explicit markers.
+In formulating our features, we assumed that like translators, L2 writers will write in a simplified manner and overuse explicit markers.
 Although this should be studied vis-a-vis comparable outputs of mother tongue writers in English, we observe that the best features of our classifiers are of the ``interference'' type, i.e.
@@
 
-We would like to stress that certain features indicating L2 do not have any bearing on the quality of the English produced, a phenomenon discussed extensively in Translation Studies \citep{Toury:1995}, where interference is observed by the overuse or underuse of certain features reflecting the typological differences between a specific pair of languages.
+We would like to stress that certain features indicating a particular L1 have no bearing on the quality of the English produced.
+This has been discussed extensively in Translation Studies \citep{Toury:1995}, where interference is observed by the overuse or underuse of certain features reflecting the typological differences between a specific pair of languages, but which is still within grammatical limits.
 For example, the fact that Italian native speakers favor the syntactic sequence of determiner + adjective + noun (e.g., \textnl{a big risk} or \textnl{this new business}) has little prescriptive value for teachers.
 
-Last, we noted that certain L2 writers tend to repeat more often words appearing in the prompts, i.e., in the questions that triggered their essays.
-When we experimented on certain classifiers with and without the prompt number as a feature, we actually noted a decrease in performance.
-For the sake of sports, we should have in fact removed them from our classifier, but we stress their theoretical importance: some L2 writers repeat them more often and this may reflect different educational backgrounds (introducing this as a feature offsets its effect).
-Had we had a hypothetical 12th unseen L2, we believe it would have enabled us to cross-classify better.
-Again, this feature says nothing about the quality of the text, just as the tendency of Korean and Italian writers to mention their home country more often does not.
+A further example of how L2 quality and the ability to predict L1 are uncorrelated, we noted that certain L2 writers often repeat words appearing in their essay prompts, and including information about whether the writer was reusing prompt words improved classification accuracy.
+We suggest this reflects different educational backgrounds.
+This feature says nothing about the quality of the text, just as the tendency of Korean and Italian writers to mention their home country more often does not.
 %\section{Conclusion}
@@
 This research was supported by a grant from the Israeli Ministry of
-Science and Technology.\nss{anything from the CMU side?}
-
-%\clearpage
+Science and Technology.
 

### 2013-04-09 paper/paper.tex
author list

@@
 \title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] 
-{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Victor Chahuneau$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
+{\large Yulia Tsvetkov$^\ast$\ Naama Twitto$^\dagger$\  Nathan Schneider$^\ast$\ Noam Ordan$^\dagger$\\ 
+Manaal Faruqui$^\ast$\  Victor Chahuneau$^\ast$\  Shuly Wintner$^\dagger$ \  Chris Dyer$^\ast$}\\[-3em]
 }

### 2013-04-10 paper/paper.tex
use official NAACL bib style and other tweaks

@@
 
-\usepackage[round]{natbib}
+%\usepackage[round]{natbib}
+\newcommand{\citep}[1]{\cite{#1}}
+\newcommand{\citet}[1]{\newcite{#1}}
+
 \setlength\titlebox{6.5cm}    % Expanding the titlebox
@@
 \newcommand{\featstr}[1]{\textsmaller[.5]{\verb|#1|}} % full feature name
-\newcommand{\textnl}{\textsl}
+\newcommand{\textnl}{\textit}
 
@@
 \label{sec:literature}
-The task of L1 identification was introduced by
-\citet{koppel2005automatically,koppel2005determining}, who work on the
+The task of L1 identification was introduced by Koppel et~al. \shortcite{koppel2005automatically,koppel2005determining}%
+%\citet{koppel2005automatically,koppel2005determining}
+, who work on the
 International Corpus of Learner English \citep{icle}, which includes
@@
 this hypothesis by carefully analyzing the features used by
-\citeauthor{koppel2005automatically}, controlling for potential
+Koppel et~al.\nocite{koppel2005automatically}%\citeauthor{koppel2005automatically}
+, controlling for potential
 biases.
 
-\citet{Wong-Dras:2009:ALTA2009,wong-dras:2011:EMNLP} are also
+Wong and Dras \shortcite{Wong-Dras:2009:ALTA2009,wong-dras:2011:EMNLP}
+%\citet{Wong-Dras:2009:ALTA2009,wong-dras:2011:EMNLP} 
+are also
 motivated by a linguistic hypothesis, namely that \emph{syntactic} errors in
@@
 features does not improve on the results of
-\citeauthor{koppel2005automatically}. \citet{wong-dras:2011:EMNLP}
+Koppel et~al.\nocite{koppel2005automatically}%\citeauthor{koppel2005automatically}
+. \citet{wong-dras:2011:EMNLP}
 further extend this work by adding as features horizontal slices of
@@
 \label{sec:model}
-For our classification model we used the \texttt{creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the classifier as a multiclass logistic regression:
+For our classification model we used the \texttt{creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{\url{https://github.com/redpony/creg}}  We parameterize the classifier as a multiclass logistic regression:
 \begin{align*}
@@
 While an $\ell_2$ weight penalty is standard in regression problems like this, we found that the the additional entropy term gave more reliable results.
-Intuitively, the entropic regularizer encourages the remain maximally uncertain about its predictions.
+Intuitively, the entropic regularizer encourages the model to remain maximally uncertain about its predictions.
 In the metaphor of ``maximum entropy'', the entropic prior finds a solution that has \emph{more} entropy than the ``maximum'' model that is compatible with the constraints.
@@
   phrases) that have a strong discourse function in texts (\textnl{however},
-  \textnl{because}, \textnl{in fact}, etc.) Translators tend to spell out implicit
+  \textnl{because}, \textnl{in fact}, etc.). Translators tend to spell out implicit
   utterances and render them explicitly in the target text
@@
   are used, like cohesive markers, to spell out implicit utterances
-  (\textnl{indicate}, \textnl{imply}, \textnl{contain}, etc.)
+  (\textnl{indicate}, \textnl{imply}, \textnl{contain}, etc.).
 \item[Function words] Frequent tokens, which are mostly function
@@
 Since English's orthography is largely phonemic---even if it is irregular in many places, we expect leaners whose native phoneme contrasts are different from those of English to make characteristic spelling errors.
-For example, since Japanese and Korean lack a phonemic /l/-/r/ contrast, we expect native speakers of those languages to be more likely to make spelling errors that confuse {\tt l} and {\tt r} relative to native speakers of languages such as Spanish in which that pair is contrastive.
+For example, since Japanese and Korean lack a phonemic /l/-/r/ contrast, we expect native speakers of those languages to be more likely to make spelling errors that confuse \textnl{l} and \textnl{r} relative to native speakers of languages such as Spanish in which that pair is contrastive.
 To make this information available to our model, we use a noisy channel spelling corrector \citep{kernighan:1990} to identify and correct misspelled words in the training and test data.
@@
 \item[\feat{Misspell}] Spelling correction edits.
-Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred.
+Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred\nss{i.e.
+beginning, middle, or end?}.
 \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
@@
 called \emph{interference} in Translation Studies \citep{Toury:1995}
-and \emph{interlanguage} in second language acquisition
+and \emph{interlanguage}\nss{do you mean `transfer'?
+I think `interlanguage' refers to the L2 as used by a nonnative speaker, and `transfer' from the L1 is one of the influences on interlanguage.} in second language acquisition
 \citep{Selinker1972}. \citet{vered:noam:shuly} designed 32 classifiers to test the validity
@@
 Arabic, being an Abjad language, rarely indicates vowels, and indeed
-we find many missing \textnl{e}-s and \textnl{i}-s in the texts of
+we find many missing \textnl{e}'s and \textnl{i}'s in the texts of
 Arabic speakers. Phonologically, because Arabic conflates
 /\textipa{I}/ and /\textipa{@}/ into /i/ (at least in Modern Standard
-Arabic), we see that many {\tt e}'s are indeed substituted for
-{\tt i}'s in these texts.
+Arabic), we see that many \textnl{e}'s are indeed substituted for
+\textnl{i}'s in these texts.
 
@@
 
-Other informative features that reflect L1 features include frequent misspellings involving confusions of {\tt l} and {\tt r} in Japanese essays.
+Other informative features that reflect L1 features include frequent misspellings involving confusions of \textnl{l} and \textnl{r} in Japanese essays.
 More mysteriously, the characters \textnl{r} and \textnl{s} are misused in Chinese
@@
 In formulating our features, we assumed that like translators, L2 writers will write in a simplified manner and overuse explicit markers.
-Although this should be studied vis-a-vis comparable outputs of mother tongue writers in English, we observe that the best features of our classifiers are of the ``interference'' type, i.e.
+Although this should be studied vis-\`{a}-vis comparable outputs of mother tongue writers in English, we observe that the best features of our classifiers are of the ``interference'' type, i.e.
 phonological, morphological and syntactic in nature, mostly in the form of misspelling features, restoration tags, punctuation and lexical and syntactic modeling.
@@
 
+\nss{comment on how we did in relation to other task participants? if I were a reader I'd want to know}
+
 \section*{Acknowledgments}
@@
 \bibliography{l1id}
-\bibliographystyle{plainnat}
+%\bibliographystyle{plainnat}
+\bibliographystyle{naaclhlt2013}
 

### 2013-04-10 paper/paper.tex
some fixes, ducttape shout-out

@@
 \end{abstract}
+
+\nss{comment on how we did in relation to other task participants? as a reader I'd want to know!}
 
@@
 \caption{Independent performance of feature types detailed in \Sref{sec:mainfeats}, \Sref{sec:addfeats} and \Sref{sec:discarded}. 
-Accuracy is averaged over 10 folds of cross-validation on the training set.}
+Accuracy is averaged over 10 folds of cross-validation on the training set.}\label{tbl:isolatedfeats}
 \end{table}
@@
 model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
-the feature's value.  \Tref{tbl:mainfeats} reports the accuracy of using each feature type in
+the feature's value.  \Tref{tbl:isolatedfeats} reports the accuracy of using each feature type in
 isolation (with 10-fold cross-validation on the training set).
@@
 The accuracy of the classifier on the development set using these four
-feature types is reported in \tref{tbl:mainfeats}.
+feature types is reported in \tref{tbl:mainfeats}.\footnote{For experiments in this paper combining multiple types of features, 
+we used Jonathan Clark's workflow management tool, \texttt{ducttape} (\url{https://github.com/jhclark/ducttape}).}
 
@@
 accuracy on the development set is~84.55\%, and on the test set it
-is~81.5\%. The values for $\alpha$ and $\tau$ were tuned to optimize development set performance, and found to be $\alpha=5$,$\tau=2$.
+is~81.5\%. The values for $\alpha$ and $\tau$ were tuned to optimize development set performance, and found to be $\alpha=5, \tau=2$.
 
@@
 
-\nss{comment on how we did in relation to other task participants? if I were a reader I'd want to know}
-
 \section*{Acknowledgments}

### 2013-04-13 paper/paper.tex
fixes

@@
 \newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
-\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
-%\newcommand{\arkcomment}[3]{}
+%\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
+\newcommand{\arkcomment}[3]{}
 \newcommand{\ignore}[1]{}
@@
 \item[\feat{Misspell}] Spelling correction edits.
-Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred\nss{i.e.
-beginning, middle, or end?}.
+Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred.
+%\nss{i.e.
+beginning, middle, or end?}
 \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
@@
 called \emph{interference} in Translation Studies \citep{Toury:1995}
-and \emph{interlanguage}\nss{do you mean `transfer'?
-I think `interlanguage' refers to the L2 as used by a nonnative speaker, and `transfer' from the L1 is one of the influences on interlanguage.} in second language acquisition
+and \emph{transfer} in second language acquisition
 \citep{Selinker1972}. \citet{vered:noam:shuly} designed 32 classifiers to test the validity

### 2013-05-16 poster/poster.tex
poster v1

\documentclass[landscape,final]{baposter}

\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{url}
\usepackage{tipa}
%\usepackage{biblatex}

\usepackage{multicol}
\usepackage{natbib}
\newcommand{\namecite}{\citet}
\renewcommand{\cite}{\citep}
\bibpunct[, ]{[}{]}{;}{n}{,}{,}

\usepackage{pgfbaselayers}
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\usepackage{helvet}
\usepackage{palatino}

\newcommand{\captionfont}{\footnotesize}
\newcommand{\hl}[1]{\color{red}{#1}}
%\newcommand{\textgl}[1]{``#1''}
%\newcommand{\word}[2]{\textnl{#1} \textgl{#2}}
%\newcommand{\gloss}[3]{\textnl{#1} (\textnl{#2}) \textgl{#3}}

%\newcommand{\upspc}{\vspace{-1.9em}}

\newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
\newcommand{\textnl}{\textsl}

\selectcolormodel{cmyk}

\graphicspath{{../}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Multicol Settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\columnsep}{0.7em}
\setlength{\columnseprule}{0mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save space in lists. Use this after the opening of the list
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\compresslist}{%
\setlength{\itemsep}{1pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Begin of Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
\background{
  \begin{tikzpicture}[remember picture,overlay]%
    \draw (current page.north west)+(-2em,-0em) node[anchor=north west] {\hspace{-2em}\includegraphics[height=1.1\textheight]{silhouettes_background}};
  \end{tikzpicture}%
}
\definecolor{silver}{cmyk}{0,0,0,0.3}
\definecolor{yellow}{cmyk}{0,0,0.9,0.0}
\definecolor{reddishyellow}{cmyk}{0,0.22,1.0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}
\definecolor{darkYellow}{cmyk}{0,0,1.0,0.5}
\definecolor{darkSilver}{cmyk}{0,0,0,0.1}

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
% My colors
\definecolor{lightmagenta}{cmyk}{0,0.3,0.0,0.0}
\definecolor{lightermagenta}{cmyk}{0,0.1,0,0.0}
\definecolor{lightestmagenta}{cmyk}{0,0.05,0.0,0.0}
\definecolor{cyan}{cmyk}{0.9,0.,0.0,0.0}
\definecolor{lightcyan}{cmyk}{0.3,0.,0.0,0.0}
\definecolor{lightercyan}{cmyk}{0.1,0,0,0.0}
\definecolor{lightestcyan}{cmyk}{0.05,0.0,0.0,0.0}
\definecolor{blue}{cmyk}{0.5,0.2,0.0,0.0}
\definecolor{lightblue}{cmyk}{0.2,0.12,0.0,0.0}
\definecolor{lighterblue}{cmyk}{0.1,0.05,0,0.0}
\definecolor{lightestblue}{cmyk}{0.01,0.005,0.0,0.0}

\definecolor{darkpurple}{cmyk}{1,1,0.0,0.0}
\definecolor{lightpurple}{cmyk}{0.1,0.4,0.0,0.0}

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=0.8em,
  % Color style
  bgColorOne=lightestcyan, %lighteryellow,
  bgColorTwo=lighterblue, %lightestyellow,
  borderColor=darkpurple, %reddishyellow,
  headerColorOne=blue, %yellow,
  headerColorTwo=darkpurple, %reddishyellow,
  headerFontColor=black,
  boxColorOne=lighterblue, %lightyellow,
  boxColorTwo=lighterblue, %lighteryellow,
  % Format of textbox
  textborder=rounded, %roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=closed,
  headerheight=0.1\textheight,
  headershape=rounded, %roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {%\begin{minipage}{7em}
\includegraphics[width=9em]{img/CarnegieMellonUniversity}\\
%\end{minipage}
} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\bf %Sans Serif
  %\bf% Serif
  Identifying the native language of non-native English writers 
  }
    % Authors
  {\large\sl %Sans Serif
  % Serif
  Chris Dyer, Manaal Faruqui, Nathan Schneider, Yulia Tsvetkov, Language Technologies Institute,
  Carnegie Mellon University, Pittsburgh, PA
  \large
  \\Noam Ordan, Naama Twitto, Shuly Wintner,
  Department of Computer Science,University of Haifa, Haifa, Israel
  }
  % University logo clip=true, trim=l b r t,
  {  \includegraphics[height=5.1em]{img/University_of_Haifa_logo} %logo1
  }
 % {  \includegraphics[height=5.1em]{img/logo1}
  %}

  \tikzstyle{light shaded}=[top color=baposterBGtwo!30!white,bottom color=baposterBGone!30!white,shading=axis,shading angle=30]

  % Width of left inset image
   %  \newlength{\leftimgwidth}
    % \setlength{\leftimgwidth}{0.78em+8.0em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position 
%%% towards an already declared box. So if you have a box attached to the 
%%% bottom, one to the top and a third one which should be in between, you 
%%% have to specify the top and bottom boxes before you specify the middle 
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    % A coloured circle useful as a bullet with an adjustably strong filling
    \newcommand{\colouredcircle}[1]{%
      \tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=bgColorOne!80!black!#1!white,line width=0.03em] (0,0) circle(0.18em);}}

    \newcommand{\numbox}[1]{%
      \tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=headerColorOne!80!black!80!white,line width=0.03em] (0,0) circle(0.5em); \path (0,0) node {\smaller #1};}\hspace{0.2em}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Abstract%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Abstract}{name=abstract,column=0,row=0,span=1}{
{\bf We show that it is possible to identify, with high accuracy, the native language of English test takers from the content of the essays they write.} %as part of the TOEFL exam.} 
We use standard machine-learning text classification techniques to %define sophisticated classifiers and% 
predict the most probable native language from a set of 11 possibilities: Arabic, Chinese, French, German, Hindi, Italian, Japanese, Korean, Spanish, Telugu, and Turkish.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%System Overview%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\headerbox{System Overview}{name=diagram,column=1,span=2}{
%This system was developed to classify each essay to one of 11-class languages. For our classification model, we use the \texttt{creg} regression modelling framework..\footnote{\url{https://github.com/redpony/creg}}  
%\begin{center}
% \includegraphics[width=0.7\textwidth]{img/diagram1}
%\end{center}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Motivation%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\headerbox{Motivation }{name=motivation,column=0,span=1, below=abstract}{
Our motivation is both to improve the accuracy of classification and to be able to interpret the characteristics of the language produced by speakers of different native languages. %Analysis of the results can shed light on the characteristics of the language produced by non-native authors.
%Except of that this task is interesting in and of itself, 
Such a system can be useful for a number of applications:

\begin{itemize}
\item Tutoring applications that can identify the native language of the writer can offer better targeted feedback to language learners about their errors, since many errors are native language-specific.

 %the different types of errors made by non-native speakers when they write English, depends on their native language \cite{lado-57,swan2001learner}. 
%System to identify the native language of the writer, can offer better targeted feedback to language learners about their errors.
\item Forensic linguistic applications often need to determine the native language of authors.
%systems, such as the one we describe, can assist determining the native language of the authors % \cite{estival-gaustad-pham-radford-hutchinson:2007:ALTA2007,estival2007author}.
\end{itemize}

}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Main Features}{name=mf,column=1, span = 2}{ 
This system was developed to classify each essay to one of 11-class languages. For our classification model, we use the \texttt{creg} regression modelling framework (\url{https://github.com/redpony/creg}).%\footnote{\url{https://github.com/redpony/creg}} 
%\linebreak 
We define a large arsenal of features. %some of them inspired by the features used to identify translationese by \cite{vered:noam:shuly}. 
The following four feature types are used as the baseline features:
\begin{description}
\item [Part-of-speech (POS) $n$-grams] Features were extracted to 
 count every POS 1-, 2-, and 3-gram in each document. %53.92\% 
\item [FreqChar] We experimented with character $n$-grams. To reduce the number of parameters, we retain only those character $n$-grams that are observed more than 5 times in the training corpus. The value of $n$ ranges from 1 to 4.
%Frequent character $n$-grams. We experimented with character $n$-grams. To reduce the number of parameters, we removed features only those character $n$-grams that are observed more than $5$ times in the training corpus, and $n$ ranges from~1 to~4.
\item [CharPrompt] Conjunction of the character $n$-gram features defined above with the prompt ID %65.09
\item [Brown clusters] Using the Brown clusters algorithm %\cite{brown:cl1992} 
we clustered 8~billion words of English into 600~classes. Then we included log counts of all $4$-grams of Brown clusters that occurred at least $100$ times in the training data.
\end{description}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Additional Features}{name=addf,column=1, span = 2,below=mf}{ 
To the basic set of features we add more specific, linguistically-motivated features such as:

\begin{description}
%\item[Position] Positional token frequency. The log counts for the first two and last three words before the period in each sentence as features.
\item[PsvRatio] The proportion of passive verbs out of all verbs.
\item[DocLen] Document length in tokens.
%\item[Pron] Log counts of each pronoun.
\item[Punct] Log counts of each punctuation mark. 
\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings (\textnl{alot}$\rightarrow$\textnl{a lot}) that were made by the author of the essay. High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>};  {\tt SPA:INS<s>}.% as well as the word position where the error occurred.
\item[CxtFxn]Contextual function words. We define pairs consisting of a function word, along with the POS tag of its adjacent word. We also define 3-grams consisting of one or two function words and the POS tag of the third word in the 3-gram.
\end{description}

}
%%Additional features:
%\begin{description}
%\item[DocLen] Document length in tokens. 11.81\%.
%\item[Punct] Counts of each punctuation mark. 27.41\%.
%\item[Pron] Counts of each pronoun. 22.81\%.
%\item[Position] Positional token frequency. We use the counts for the first two and last three words before the period in each sentence as features. 53.03\%.
%\item[PsvRatio] The proportion of passive verbs out of all verbs. 12.26\%.
%\item[CxtFxn] Contextual function words. Bi-grams yield 62.79\%, tri-gram 62.32\%.
%\item[Misspell] Spelling correction edits. ???. 37.29\%.
%\item[Restore] Counts of substitutions, deletions and insertions of predefined tokens that we restored in the texts. 47.67\
%\end{description}
%
%\begin{center}
%\begin{tabular}{lrc}
%\small
%\textbf{Feature Group} & \multicolumn{1}{c}{\# Params}  & \multicolumn{1}{c}{Accuracy(\%)} \\\hline
%%\feat{POS} & 540,947 & 55.18 \\
%\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
%\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
%\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
%\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
%\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
%\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
%\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
%%+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
%%\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
%%\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
%\end{tabular}
%\end{center}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \headerbox{Accuracy}{name=results,column=3,span=1}{
The full model that we used to classify the test set combines all features. %The accuracy of the full model on the test set is 81.5\%. %listed in \tref{tbl:addfeats}. 
%In this model, the accuracy  for 10-fold cross-validation on the development set is {\bf ~84.55\% }, and on the test set it is~81.5\%. %most of the additional features exhibited negligible improvement.

\begin{center}
\begin{tabular}{|l|c|c|c|}
      \hline
 \multirow{2}{*} {} Feature Group & \# Params 	& Accuracy(\%)	\\				
       \hline\hline
\feat{POS} & 540,947 & 55.18 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
			\hline%\hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|l|c|c|c|}
      \hline
 \multirow{2}{*} {} Feature Group & \# Params 	& Accuracy(\%)	\\				
       \hline\hline
\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
%\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
\textsc{full model} & - & {\bf 84.55} \\

			\hline%\hline
\end{tabular}
\end{center}
\begin{center}
The accuracy for 10-fold cross-validation on the development set.
\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Datasets%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \headerbox{Datasets}{name=dataset,column=0,span=1,below=motivation}{

The dataset consists of 12,100 English TOEFL essays written by speakers of 11 different languages, distributed as part of the First Native Language Identification Shared Task. Each essay is labelled with the author's English language proficiency level (high, medium, or low) and an identification (1 to 8) of the essay prompt.
%The dataset consists of TOEFL 12,100 English essays written by speakers of 11 different languages, 
%\cite{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR}, 
%distributed as part of the First Native Language Identification Shared Task %\cite{tetreault-blanchard-cahill:2013:BEA}.
%Each essay is labelled with the author's English language proficiency level (high, medium, or low) and an identification (1 to 8) of the essay prompt. %The essays are short, consisting of 10 to 20 sentences each. %(300 to 400 tokens). %We use 9,900 documents for training, 1,100 for development and 1,100 as a test set

%\begin{center}
%\begin{tabular}{|l|r|r|}
%\textbf{Data} & \multicolumn{1}{c}{\# essays} \\\hline
%Training & 9,900\\
%Development  & 1,100 \\
%Testing  &  1,100 \\
%\end{tabular}
%\end{center}

\begin{center}
\begin{tabular}{|l|c|}
      \hline
 \multirow{2}{*}{} Data & \# essays \\				
      \hline\hline
      Training			& 9,900	 \\	
      Development			& 1,100 \\		
      Testing	& 1,100	\\	
			\hline%\hline
\end{tabular}
\end{center}
\begin{center}
Number of essays per dataset.
\end{center}

\begin{center}
\begin{tabular}{|l|r|r|r|}
      \hline
 \multirow{2}{*}{} & Low 	& Medium 		& High \\				
      \hline\hline
      Essays			& 1,069 			& 5,366 			& 3,456 \\	
      Tokens			& 245,130 			& 1,819,407 			& 	1,388,260	\\	
      Types			& 13,110 			& 37,393 			&  	28,329	\\	
			\hline%\hline
\end{tabular}
\end{center}
\begin{center}
Corpus size per author's proficiency level.
\end{center}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results Analysis%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Analysis}{name=analysis,column=3,span=1,below=results}{
 % \scriptsize 
Texts produced by non native English writers involves a tension between the imposing models of the native language, on the one hand, and a set of cognitive constraints resulting from the efforts to generate the target text, on the other. 
The former is called \emph{interference} in Translation Studies. %\cite{Toury:1995}. 
%\linebreak
We explore the effects of interference by analysing several patterns we observe in the features.

\begin{itemize}
\item Arabic speakers use \textnl{a lot} as a single word more often and sometime omit the definite article before nouns and adjectives. 
\item German authors use Hyphens more frequently, probably due to compounding in their native language. They also tend to substitute the letter \textnl{y} with \textnl{z} and vice versa.
%German authors use Hyphens more frequently and tending to substitute the letter \textnl{y} with \textnl{z} and vice versa. We suspect this owes to their switched positions on German keyboards. 
\item Japanese authors confuse \textnl{l} and \textnl{r}.
\item The characters \textnl{r} and \textnl{s} are misused in Chinese
and Spanish, respectively.
%\item The word \textnl{then} is dominant in the texts of Hindi speakers.
\end{itemize}

%\begin{itemize}
%\item Character sequence \textnl{alot} is overrepresented in English written by Arabic speakers.  %and we speculate that Arabic speakers conceive \textnl{a lot} as a single word; For the same reason, another prominent feature is 
%\item A missing definite article before nouns and adjectives. Arabic has no indefinite article.
%\item Essays that contain hyphens are more likely to be from German authors. 
%\item Essays by native Germans is a frequent substitution of the letter \textnl{y} for \textnl{z} and vice versa. We suspect this owes to their switched positions on German keyboards.
%%Another unexpected feature of essays by native Germans is a frequent substitution of the letter \textnl{y} for \textnl{z} and vice versa. We suspect this owes to their switched positions on German keyboards. 
%\item Frequent misspellings involving confusions of \textnl{l} and \textnl{r} in Japanese essays.
%\end{itemize}
}

\headerbox{Results}{name=tsclass,column=1,span=2,below=addf}{
%\begin{description}
%\item [] %%% 
%\end{description}

\begin{center}
\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
 \multirow{2}{*}{} &ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR  \\				
      \hline\hline
ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1  \\
\hline
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3  \\
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 \\
\hline
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4  \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2  \\
\hline
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0  \\
\hline
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5  \\
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3  \\
%\hline
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80  \\
			\hline%\hline
\end{tabular}
\end{center}
\begin{center}
Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%
\end{center}

%\begin{center}
%\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|}
%\hline
%%\small
%\multirow{2}{*}{} & ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR & \\				
%\hline\hline
%ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0 & 80.4 \\
%CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0 & 84.2 \\
%FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0 & 83.5 \\
%%\hline
%GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0 & 90.3 \\
%HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0 & 75.9 \\
%ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0 & 84.5 \\
%%\hline
%JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 & 82.5 \\
%KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0 & 80.6 \\
%SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0 & 77.6 \\
%%\hline
%TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0 & 78.9 \\
%TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0 & 78.4 \\
%\hline\hline
%\end{tabular}
%\end{center}
%\begin{center}
%C
%\end{center}

%\begin{center}
%%\begin{tabular}{>{\bf}l|r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r|ccc}
%\begin{tabular}{l|rrrrrrrrrrr|ccc}
%\small
%& \bf ARA & \bf CHI & \bf FRE & \bf GER & \bf HIN & \bf ITA & \bf JPN & \bf KOR & \bf SPA & \bf TEL & \bf TUR & \bf Precision (\%) & \bf Recall (\%) & \bf $F_1$ (\%) \\
%\hline
%ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0 & 80.4 \\
%CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0 & 84.2 \\
%FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0 & 83.5 \\
%\hline
%GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0 & 90.3 \\
%HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0 & 75.9 \\
%ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0 & 84.5 \\
%\hline
%JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 & 82.5 \\
%KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0 & 80.6 \\
%SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0 & 77.6 \\
%\hline
%TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0 & 78.9 \\
%TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0 & 78.4 \\
%\end{tabular}
%\end{center}

%\begin{center}
% \includegraphics[width=0.67\textwidth]{img/graph}
%\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%References%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\headerbox{References}{name=references,column=3,span=1,below=analysis}{
%    \smaller
%    \vspace{-1.2em}
%    \renewcommand{\refname}{}
%\bibliographystyle{plainnat}
%\bibliography{l1id}
%  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Acknowledgements%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Acknowledgements}{name=ack,column=3,span=1,below=analysis}{
%\scriptsize 
    This research was supported by a grant from the Israeli Ministry of Science and Technology.  
}

\end{poster}%
\end{document}

### 2013-05-16 poster/poster.tex
poster v2

@@
 \usepackage{palatino}
-
+\usepackage{listings}
 \newcommand{\captionfont}{\footnotesize}
@@
 \newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
-\newcommand{\textnl}{\textsl}
+%\newcommand{\featstr}[1]{\textsmaller[.5]{\begin{lstlisting}#1\end{lstlisting}}} % full feature name
+\newcommand{\textnl}{\textit}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Abstract%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Abstract}{name=abstract,column=0,row=0,span=1}{
-{\bf We show that it is possible to identify, with high accuracy, the native language of English test takers from the content of the essays they write.} %as part of the TOEFL exam.} 
-We use standard machine-learning text classification techniques to %define sophisticated classifiers and% 
-predict the most probable native language from a set of 11 possibilities: Arabic, Chinese, French, German, Hindi, Italian, Japanese, Korean, Spanish, Telugu, and Turkish.
+\headerbox{Abstract}{name=abstract,column=0,row=0,span=1.15}{
+{\bf We show that it is possible to identify, with high accuracy, the native language of English test takers from the content of the essays they write.} 
+Our method uses standard text classification techniques based on multiclass logistic regression, combining individually weak indicators to predict the most probable native language from a set of 11 possibilities: Arabic, Chinese, French, German, Hindi, Italian, Japanese, Korean, Spanish, Telugu, and Turkish.
 }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%System Overview%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\headerbox{System Overview}{name=diagram,column=1,span=2}{
-%This system was developed to classify each essay to one of 11-class languages.
-For our classification model, we use the \texttt{creg} regression modelling framework..\footnote{\url{https://github.com/redpony/creg}}
-%\begin{center}
-% \includegraphics[width=0.7\textwidth]{img/diagram1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\headerbox{Features}{name=features,column=0,span=1.15,below=abstract}{
+For our classification model, we use the \texttt{creg} \\\url{https://github.com/redpony/creg}
+%\linebreak
+
+\begin{description}
+\item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
+\item [FreqChar] Counts of character $n$-grams that are observed more than 5 times in the training corpus. $n$ ranges from~1 to~4.
+\item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
+\item [Brown clusters] We clustered 8~billion words of English into 600~clusters of words that appear in similar left and right contexts.
+(\url{http://www.ark.cs.cmu.edu/cdyer/en-600/cluster_viewer.html}).
+Our features are counts of $n$-grams of Brown clusters as lexical representations.
+$n$ ranges from~1 to~4.
+\item[PsvRatio] The proportion of passive verbs out of all verbs.
+\item[DocLen] Document length in tokens.
+\item[Punct] Counts of each punctuation mark. 
+\item[Misspell] Spelling correction edits.
+Features included substitutions, deletions, insertions and joinings (\textnl{alot}$\rightarrow$\textnl{a lot}) that were made by the author of the essay.
+High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:INS<s>}.% as well as the word position where the error occurred.
+\item[\feat{Restore}] Counts of substitutions, deletions and
+  insertions of predefined tokens that we restored in the texts: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}.%; {\tt ITA:DELWORD<be>} 
+\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}.
+
+\end{description}
+}  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Example%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\headerbox{Example: L1 German sentence}{name=example,column=1.15,span = 1.85}{ 
+%We focus on two broad novel categories of features: those inspired by the features used to identify translationese and those extracted by automatic statistical ``correction'' of the essays.
+
+\centering\small
+\vspace{4pt}
+\textbf{Firstly the employers live more savely because they are going to have more money to spend for luxury .}\\[14pt]
+
+\begin{tabular}{p{6em}p{15em}p{15em}}
+ & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
+\hline
+\bf Characters
+& 
+\smaller[.5]
+ \begin{tabular}{@{}p{12em}p{5em}@{}} 
+   "FreqChar\_l\_y\_ ":&$\log{2+1}$\\"CharPrompt\_P5\_g\_o\_i":&$\log{1+1}$\\"Punct\_period":&$\log{1+1}$ %\\"MFChar\_e\_ ":&$\log{1+1}$
+ \end{tabular} 
+& 
+\smaller[.5]
+ \begin{tabular}{@{}p{12em}p{5em}@{}} 
+   "Misspell\_DeleteP\_p\_.":&$1.0$\\"Misspell\_InsertP\_p\_,":& $1.0$\\"Misspell\_MID:SUBST:v:f":&$\log{1+1}$\\"Misspell\_SUBST:v:f":&$\log{1+1}$
+ \end{tabular} \\
+\hline
+\bf Words 
+& 
+\smaller[.5]
+ \begin{tabular}{@{}p{12em}p{5em}@{}}
+    "DocLen\_":&$\log{19+1}$\\"MeanWordRank":&$422.6$\\"CohMarker\_because":&$\log{1+1}$\\"MostFreq\_have":&$\log{1+1}$\\"PosToken\_last\_luxury":&$\log{1+1}$\\ "Pronouns\_they":&$\log{1+1}$
+ \end{tabular}
+& 
+\smaller[.5]
+ \begin{tabular}{@{}p{12em}p{5em}@{}}
+   "Misspell\_safely":&$\log{1+1}$\\"Restore\_Match\_p\_to":&$0.5$\\"Restore\_Delete\_p\_to":&$0.5$\\"Restore\_Delete\_p\_are":&$1.0$\\"Restore\_Delete\_p\_because":&$1.0$\\"Restore\_Delete\_p\_for":&$1.0$
+ \end{tabular} \\
+\hline
+\bf{POS} 
+& 
+\smaller[.5]
+\begin{tabular}{@{}p{12em}p{5em}@{}}
+  "POS\_VBP\_VBG\_TO":&$\log{1+1}$\\"POS\_p\_VBP\_VBG\_TO":&$0.059$
+\end{tabular} \\
+\hline
+\bf Words + POS 
+& 
+\smaller[.5]
+\begin{tabular}{@{}p{12em}p{5em}@{}}
+  "CxtFxn\_VBP\_VBG\_to":&$\log{1+1}$\\"CxtFxn\_more\_RB":&$\log{1+1}$
+\end{tabular} \\
+\hline
+
+\bf Brown
+& 
+\smaller[.5]
+\begin{tabular}{@{}p{30.5em}p{5em}@{}}
+  "C\_1111101111110\_110100011110\_110101101100":
+  & $\log{1+1}$\\
+
+\end{tabular} \\\\[14pt]
+
+\end{tabular}
+
+\begin{tabular}{p{10em}p{32em}}
+  \multicolumn{1}{c}{\bf Brown clusters} & \multicolumn{1}{c}{\bf Words in cluster}\\\hline
+ C\_1111101111110   & investors customers patients employees consumers users citizens shareholders clients individuals managers buyers viewers \textbf{employers} guests readers immigrants taxpayers humans donors households homeowners competitors travelers audiences borrowers shoppers offenders physicians creditors subscribers stockholders sellers entrepreneurs advertisers applicants motorists tenants builders smokers strangers collectors listeners savers retirees outsiders travellers bidders bondholders patrons\\ \hline
+
+ C\_110100011110   & \textbf{live} remain stay stand die sit compete operate invest participate arrive engage succeed lie cope gather testify comply communicate proceed weigh disagree cooperate intervene expire rein behave interact thrive interfere prevail persist coincide explode collaborate linger grips enroll indulge resonate dine tread prosper loom grapple reside retaliate collide regroup innovate \\ \hline
+
+  C\_110101101100   & \textbf{more} less fewer ... \\\\
+
+ \end{tabular} 
+% \begin{center}
+%Some of the features extracted for an L1 German sentence.
 %\end{center}
-%}
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Motivation%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\headerbox{Motivation }{name=motivation,column=0,span=1, below=abstract}{
-Our motivation is both to improve the accuracy of classification and to be able to interpret the characteristics of the language produced by speakers of different native languages.
-%Analysis of the results can shed light on the characteristics of the language produced by non-native authors.
-%Except of that this task is interesting in and of itself, 
-Such a system can be useful for a number of applications:
-
-\begin{itemize}
-\item Tutoring applications that can identify the native language of the writer can offer better targeted feedback to language learners about their errors, since many errors are native language-specific.
-
- %the different types of errors made by non-native speakers when they write English, depends on their native language \cite{lado-57,swan2001learner}. 
-%System to identify the native language of the writer, can offer better targeted feedback to language learners about their errors.
-\item Forensic linguistic applications often need to determine the native language of authors.
-%systems, such as the one we describe, can assist determining the native language of the authors % \cite{estival-gaustad-pham-radford-hutchinson:2007:ALTA2007,estival2007author}.
-\end{itemize}
-
-}  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Main Features}{name=mf,column=1, span = 2}{ 
-This system was developed to classify each essay to one of 11-class languages.
-For our classification model, we use the \texttt{creg} regression modelling framework (\url{https://github.com/redpony/creg}).%\footnote{\url{https://github.com/redpony/creg}}
-%\linebreak 
-We define a large arsenal of features. %some of them inspired by the features used to identify translationese by \cite{vered:noam:shuly}. 
-The following four feature types are used as the baseline features:
-\begin{description}
-\item [Part-of-speech (POS) $n$-grams] Features were extracted to 
- count every POS 1-, 2-, and 3-gram in each document. %53.92\% 
-\item [FreqChar] We experimented with character $n$-grams.
-To reduce the number of parameters, we retain only those character $n$-grams that are observed more than 5 times in the training corpus.
-The value of $n$ ranges from 1 to 4.
-%Frequent character $n$-grams.
-We experimented with character $n$-grams.
-To reduce the number of parameters, we removed features only those character $n$-grams that are observed more than $5$ times in the training corpus, and $n$ ranges from~1 to~4.
-\item [CharPrompt] Conjunction of the character $n$-gram features defined above with the prompt ID %65.09
-\item [Brown clusters] Using the Brown clusters algorithm %\cite{brown:cl1992} 
-we clustered 8~billion words of English into 600~classes. Then we included log counts of all $4$-grams of Brown clusters that occurred at least $100$ times in the training data.
-\end{description}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\headerbox{Results}{name=results,column=1.15,span=1.85,below=example}{
+\begin{center}
+\small
+\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r||c|c|}
+      \hline
+ \multirow{2}{*}{} &ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR	& \bf P(\%) & \bf R(\%)  \\			
+      \hline\hline
+ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
+CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
+\hline
+FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
+GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
+\hline
+HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
+ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
+\hline
+JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
+KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
+\hline
+SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
+TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0   \\
+%\hline
+TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
+			\hline%\hline
+\end{tabular}
+\end{center}
+\begin{center}
+Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%\\
+\end{center}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Additional Features}{name=addf,column=1, span = 2,below=mf}{ 
-To the basic set of features we add more specific, linguistically-motivated features such as:
-
-\begin{description}
-%\item[Position] Positional token frequency. The log counts for the first two and last three words before the period in each sentence as features.
-\item[PsvRatio] The proportion of passive verbs out of all verbs.
-\item[DocLen] Document length in tokens.
-%\item[Pron] Log counts of each pronoun.
-\item[Punct] Log counts of each punctuation mark. 
-\item[Misspell] Spelling correction edits.
-Features included substitutions, deletions, insertions and joinings (\textnl{alot}$\rightarrow$\textnl{a lot}) that were made by the author of the essay.
-High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>};  {\tt SPA:INS<s>}.% as well as the word position where the error occurred.
-\item[CxtFxn]Contextual function words.
-We define pairs consisting of a function word, along with the POS tag of its adjacent word.
-We also define 3-grams consisting of one or two function words and the POS tag of the third word in the 3-gram.
-\end{description}
-
-}
 %%Additional features:
@@
       \hline
- \multirow{2}{*} {} Feature Group & \# Params 	& Accuracy(\%)	\\				
+ \multirow{2}{*} {} Main features & \# Params 	& Accuracy(\%)	\\				
        \hline\hline
@@
       \hline
- \multirow{2}{*} {} Feature Group & \# Params 	& Accuracy(\%)	\\				
+ \multirow{2}{*} {} Additional features & \# Params 	& Accuracy(\%)	\\				
        \hline\hline
@@
 \textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
-%\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
+\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
 \textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
@@
 \begin{center}
-The accuracy for 10-fold cross-validation on the development set.
+10-fold cross-validation on the development set.
 \end{center}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Datasets%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-  \headerbox{Datasets}{name=dataset,column=0,span=1,below=motivation}{
-
-The dataset consists of 12,100 English TOEFL essays written by speakers of 11 different languages, distributed as part of the First Native Language Identification Shared Task.
-Each essay is labelled with the author's English language proficiency level (high, medium, or low) and an identification (1 to 8) of the essay prompt.
-%The dataset consists of TOEFL 12,100 English essays written by speakers of 11 different languages, 
-%\cite{blanchard-tetreault-higgins-cahill-chodorow:2013:TOEFL11-RR}, 
-%distributed as part of the First Native Language Identification Shared Task %\cite{tetreault-blanchard-cahill:2013:BEA}.
-%Each essay is labelled with the author's English language proficiency level (high, medium, or low) and an identification (1 to 8) of the essay prompt.
-%The essays are short, consisting of 10 to 20 sentences each.
-%(300 to 400 tokens).
-%We use 9,900 documents for training, 1,100 for development and 1,100 as a test set
-
-%\begin{center}
-%\begin{tabular}{|l|r|r|}
-%\textbf{Data} & \multicolumn{1}{c}{\# essays} \\\hline
-%Training & 9,900\\
-%Development  & 1,100 \\
-%Testing  &  1,100 \\
-%\end{tabular}
-%\end{center}
-
-\begin{center}
-\begin{tabular}{|l|c|}
-      \hline
- \multirow{2}{*}{} Data & \# essays \\				
-      \hline\hline
-      Training			& 9,900	 \\	
-      Development			& 1,100 \\		
-      Testing	& 1,100	\\	
-			\hline%\hline
-\end{tabular}
-\end{center}
-\begin{center}
-Number of essays per dataset.
-\end{center}
-
-\begin{center}
-\begin{tabular}{|l|r|r|r|}
-      \hline
- \multirow{2}{*}{} & Low 	& Medium 		& High \\				
-      \hline\hline
-      Essays			& 1,069 			& 5,366 			& 3,456 \\	
-      Tokens			& 245,130 			& 1,819,407 			& 	1,388,260	\\	
-      Types			& 13,110 			& 37,393 			&  	28,329	\\	
-			\hline%\hline
-\end{tabular}
-\end{center}
-\begin{center}
-Corpus size per author's proficiency level.
-\end{center}
-
 }
@@
  % \scriptsize 
-Texts produced by non native English writers involves a tension between the imposing models of the native language, on the one hand, and a set of cognitive constraints resulting from the efforts to generate the target text, on the other.
+Texts produced by non native English writers involve a tension between the imposing models of the native language, on the one hand, and a set of cognitive constraints resulting from the efforts to generate the target text, on the other.
 The former is called \emph{interference} in Translation Studies. %\cite{Toury:1995}. 
 %\linebreak
-We explore the effects of interference by analysing several patterns we observe in the features.
+We explore the effects of interference by analyzing several patterns we observe in the features.
 
@@
 \item Arabic speakers use \textnl{a lot} as a single word more often and sometime omit the definite article before nouns and adjectives. 
-\item German authors use Hyphens more frequently, probably due to compounding in their native language. They also tend to substitute the letter \textnl{y} with \textnl{z} and vice versa.
+\item German authors use hyphens more frequently, probably due to compounding in their native language. They also tend to substitute the letter \textnl{y} with \textnl{z} and vice versa.
 %German authors use Hyphens more frequently and tending to substitute the letter \textnl{y} with \textnl{z} and vice versa. We suspect this owes to their switched positions on German keyboards. 
@@
 }
-
-\headerbox{Results}{name=tsclass,column=1,span=2,below=addf}{
-%\begin{description}
-%\item [] %%% 
-%\end{description}
-
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|}
-      \hline
- \multirow{2}{*}{} &ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR  \\				
-      \hline\hline
-ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 \\
-CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1  \\
-\hline
-FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3  \\
-GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 \\
-\hline
-HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4  \\
-ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2  \\
-\hline
-JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 \\
-KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0  \\
-\hline
-SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5  \\
-TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3  \\
-%\hline
-TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80  \\
-			\hline%\hline
-\end{tabular}
-\end{center}
-\begin{center}
-Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%
-\end{center}
 
@@
 %\end{center}
-}
 

### 2013-05-17 poster/poster.tex
chris edit

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\headerbox{Model}{name=model,column=0,span=1.15,below=abstract}{
+We use a logistic regression model implemented by \texttt{creg} trained to maximize log-likelihood, penalized by a combined $\ell_2$ and entropic regularizer.
+\begin{align*}
+\hat{\boldsymbol{\lambda}} = \arg \min_{\boldsymbol{\lambda}} \alpha \overbrace{\sum_j \lambda_j^2}^{\textrm{$\ell_2$ reg.}} - \sum_{\{(\textbf{x}_i,y_i )\}_{i=1}^{|\mathcal{D}|}} \Big(& \overbrace{\log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}^{\textrm{log likelihood}}  + \\
+& \vspace{-1cm} \tau \underbrace{\mathbb{E}_{p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)} \log p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)}_{-\textrm{conditional entropy}}\Big)
+\end{align*}
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Features}{name=features,column=0,span=1.15,below=abstract}{
-For our classification model, we use the \texttt{creg} \\\url{https://github.com/redpony/creg}
+\headerbox{Features}{name=features,column=0,span=1.15,below=model}{
 %\linebreak
@@
 \item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
-\item [FreqChar] Counts of character $n$-grams that are observed more than 5 times in the training corpus. $n$ ranges from~1 to~4.
+\item [FreqChar] Counts of character 1--4-grams that are observed more than 5 times in the training corpus.
 \item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
-\item [Brown clusters] We clustered 8~billion words of English into 600~clusters of words that appear in similar left and right contexts.
-(\url{http://www.ark.cs.cmu.edu/cdyer/en-600/cluster_viewer.html}).
-Our features are counts of $n$-grams of Brown clusters as lexical representations.
-$n$ ranges from~1 to~4.
+\item [Brown clusters] We clustered 8~billion words of English into 600~clusters and used 1--4-grams.
 \item[PsvRatio] The proportion of passive verbs out of all verbs.
@@
 \item[Punct] Counts of each punctuation mark. 
-\item[Misspell] Spelling correction edits.
-Features included substitutions, deletions, insertions and joinings (\textnl{alot}$\rightarrow$\textnl{a lot}) that were made by the author of the essay.
-High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:INS<s>}.% as well as the word position where the error occurred.
-\item[\feat{Restore}] Counts of substitutions, deletions and
-  insertions of predefined tokens that we restored in the texts: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}.%; {\tt ITA:DELWORD<be>} 
-\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}.
+\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings.% as well as the word position where the error occurred.
+\item[\feat{Restore}] Substitutions, deletions and
+  insertions of common words that were restored with an $n$-gram LM.
+\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}.
 

### 2013-05-17 poster/poster.tex
chris edit

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Model}{name=model,column=0,span=1.15,below=abstract}{
-We use a logistic regression model implemented by \texttt{creg} trained to maximize log-likelihood, penalized by a combined $\ell_2$ and entropic regularizer.
+\headerbox{Classification Model}{name=model,column=0,span=1.15,below=abstract}{
+We use a logistic regression classifier implemented by \texttt{creg} trained to maximize the log-likelihood of the training data, penalized by a combined $\ell_2$ and entropic regularizer.
 \begin{align*}

### 2013-05-26 poster/poster.tex
haifa logo
cmu logo
design

@@
 
-\usepackage{times}
+%\usepackage{times}
 \usepackage{calc}
@@
 
-\usepackage{helvet}
-\usepackage{palatino}
+\usepackage{fourier} % utopia font
+\renewcommand*\sfdefault{uop} % optima font
+%\usepackage{palatino}
 \usepackage{listings}
@@
 }
-\definecolor{silver}{cmyk}{0,0,0,0.3}
+\definecolor{silver}{cmyk}{0,0,0,0.5}
+\definecolor{lightgray}{cmyk}{0,0,0,0.05}
 \definecolor{yellow}{cmyk}{0,0,0.9,0.0}
@@
   % Column spacing
-  colspacing=0.8em,
+  colspacing=1.4em,
   % Color style
-  bgColorOne=lightestcyan, %lighteryellow,
-  bgColorTwo=lighterblue, %lightestyellow,
-  borderColor=darkpurple, %reddishyellow,
-  headerColorOne=blue, %yellow,
+  bgColorOne=white, %lighteryellow,
+  bgColorTwo=white, %lightestyellow,
+  borderColor=lightgray, %reddishyellow,
+  headerColorOne=red, %yellow,
   headerColorTwo=darkpurple, %reddishyellow,
-  headerFontColor=black,
-  boxColorOne=lighterblue, %lightyellow,
-  boxColorTwo=lighterblue, %lighteryellow,
+  headerFontColor=white,
+  boxColorOne=lightgray, %lightyellow,
+  boxColorTwo=lightgray, %lighteryellow,
   % Format of textbox
-  textborder=rounded, %roundedleft,
+  textborder=rounded-small, %roundedleft,
   % Format of text header
@@
   headershade=plain,
-  headerfont=\Large\textsf, %Sans Serif
+  headerfont=\large\bf\sc\textsf, %Sans Serif
   boxshade=plain,
@@
   background=plain,
-  linewidth=2pt
+  linewidth=1pt
 }
@@
   {%\begin{minipage}{7em}
-\includegraphics[width=9em]{img/CarnegieMellonUniversity}\\
+\includegraphics[width=9em]{img/cmu_logo}\\
 %\end{minipage}
@@
   %\bf% Serif
-  Identifying the native language of non-native English writers
+  \textsf{Identifying the L1 of Non-native Writers: The CMU-Haifa System}
   }
     % Authors
-  {\large\sl %Sans Serif
+  {\large %\it %Sans Serif
   % Serif
-  Chris Dyer, Manaal Faruqui, Nathan Schneider, Yulia Tsvetkov, Language Technologies Institute,
-  Carnegie Mellon University, Pittsburgh, PA
-  \large
-  \\Noam Ordan, Naama Twitto, Shuly Wintner,
-  Department of Computer Science,University of Haifa, Haifa, Israel
+  Yulia Tsvetkov$\overset{^\textsc{c}}{\textrm{,}}$ Naama Twitto$\overset{^\textsc{h}}{\textrm{,}}$ Nathan Schneider$\overset{^\textsc{c}}{\textrm{,}}$ Noam Ordan$\overset{^\textsc{h}}{\textrm{,}}$ 
+  Manaal Faruqui$\overset{^\textsc{c}}{\textrm{,}}$ Victor Chahuneau$\overset{^\textsc{c}}{\textrm{,}}$ Shuly Wintner$\overset{^\textsc{h}}{\textrm{,}}$ and Chris Dyer$\overset{^\textsc{c}}{\textrm{}}$
+  \\
+  Language Technologies Institute,
+  \textbf{C}arnegie Mellon University, Pittsburgh, PA
+  $\bullet$ Department of Computer Science, University of \textbf{H}aifa, Haifa, Israel
   }
   % University logo clip=true, trim=l b r t,
-  {  \includegraphics[height=5.1em]{img/University_of_Haifa_logo} %logo1
+  {  \includegraphics[height=5.1em]{img/haifa_univ_logo} %logo1
   }
@@
 
-\centering\small
 \vspace{4pt}
-\textbf{Firstly the employers live more savely because they are going to have more money to spend for luxury .}\\[14pt]
+\begin{center}
+\textsf{\large Firstly the employers live more savely because they~are~going~to~have~more~money~to~spend~for~luxury~.}
+\end{center}
+\hspace{1em}Some of the features extracted:
 
-\begin{tabular}{p{6em}p{15em}p{15em}}
+\begin{center}\small
+\begin{tabular}{p{6.5em}p{17em}p{17em}}
  & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
@@
 \smaller[.5]
- \begin{tabular}{@{}p{12em}p{5em}@{}} 
+ \begin{tabular}{p{12em}p{5em}} 
    "FreqChar\_l\_y\_ ":&$\log{2+1}$\\"CharPrompt\_P5\_g\_o\_i":&$\log{1+1}$\\"Punct\_period":&$\log{1+1}$ %\\"MFChar\_e\_ ":&$\log{1+1}$
@@
 \smaller[.5]
- \begin{tabular}{@{}p{12em}p{5em}@{}} 
+ \begin{tabular}{p{12em}p{5em}} 
    "Misspell\_DeleteP\_p\_.":&$1.0$\\"Misspell\_InsertP\_p\_,":& $1.0$\\"Misspell\_MID:SUBST:v:f":&$\log{1+1}$\\"Misspell\_SUBST:v:f":&$\log{1+1}$
@@
 \smaller[.5]
- \begin{tabular}{@{}p{12em}p{5em}@{}}
+ \begin{tabular}{p{12em}p{5em}}
     "DocLen\_":&$\log{19+1}$\\"MeanWordRank":&$422.6$\\"CohMarker\_because":&$\log{1+1}$\\"MostFreq\_have":&$\log{1+1}$\\"PosToken\_last\_luxury":&$\log{1+1}$\\ "Pronouns\_they":&$\log{1+1}$
@@
 \smaller[.5]
- \begin{tabular}{@{}p{12em}p{5em}@{}}
+ \begin{tabular}{p{12em}p{5em}}
    "Misspell\_safely":&$\log{1+1}$\\"Restore\_Match\_p\_to":&$0.5$\\"Restore\_Delete\_p\_to":&$0.5$\\"Restore\_Delete\_p\_are":&$1.0$\\"Restore\_Delete\_p\_because":&$1.0$\\"Restore\_Delete\_p\_for":&$1.0$
@@
 \smaller[.5]
-\begin{tabular}{@{}p{12em}p{5em}@{}}
+\begin{tabular}{p{12em}p{5em}}
   "POS\_VBP\_VBG\_TO":&$\log{1+1}$\\"POS\_p\_VBP\_VBG\_TO":&$0.059$
@@
 \smaller[.5]
-\begin{tabular}{@{}p{12em}p{5em}@{}}
+\begin{tabular}{p{12em}p{5em}}
   "CxtFxn\_VBP\_VBG\_to":&$\log{1+1}$\\"CxtFxn\_more\_RB":&$\log{1+1}$
@@
 
-\end{tabular} \\\\[14pt]
+\end{tabular} \\[4pt]
 
 \end{tabular}
+\end{center}
 
-\begin{tabular}{p{10em}p{32em}}
+\begin{center}\small
+\begin{tabular}{p{8em}p{40em}}
   \multicolumn{1}{c}{\bf Brown clusters} & \multicolumn{1}{c}{\bf Words in cluster}\\\hline
@@
  \end{tabular}
+\end{center} 
 % \begin{center}
@@
 \small
-\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r||c|c|}
-      \hline
- \multirow{2}{*}{} &ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR	& \bf P(\%) & \bf R(\%)  \\			
-      \hline\hline
+\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r||c|c|}
+      %\hline
+ \multicolumn{1}{c}{} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
+ & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
+ &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P(\%)} & \multicolumn{1}{c}{\bf R(\%)}  \\			
+      \cline{2-14} %\hline
 ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
 CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
-\hline
+\cline{2-14}
 FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
 GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
-\hline
+\cline{2-14}
 HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
 ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
-\hline
+\cline{2-14}
 JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
 KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
-\hline
+\cline{2-14}
 SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
@@
 TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
-			\hline%\hline
+			\cline{2-14}%\hline
 \end{tabular}
@@
 \begin{center}
-Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%\\
+Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%.\\
 \end{center}
@@
 
-\begin{center}
-\begin{tabular}{|l|c|c|c|}
-      \hline
- \multirow{2}{*} {} Main features & \# Params 	& Accuracy(\%)	\\				
-       \hline\hline
+\begin{center}\small
+\begin{tabular}{|l|r|c|}
+      %\hline
+ \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy(\%)}	\\				
+       \hline %\hline
 \feat{POS} & 540,947 & 55.18 \\
@@
 
-\begin{center}
-\begin{tabular}{|l|c|c|c|}
-      \hline
- \multirow{2}{*} {} Additional features & \# Params 	& Accuracy(\%)	\\				
-       \hline\hline
+\begin{center}\small
+\begin{tabular}{|l|c|c|}
+      %\hline
+ \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy(\%)}	\\				
+       \hline %\hline
 \textsc{main} & 5,664,461 & 81.09 \\

### 2013-05-26 poster/poster.tex
alot
space before (%)

@@
  & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
- &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P(\%)} & \multicolumn{1}{c}{\bf R(\%)}  \\			
+ &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P (\%)} & \multicolumn{1}{c}{\bf R (\%)}  \\			
       \cline{2-14} %\hline
@@
 %\small
-%\textbf{Feature Group} & \multicolumn{1}{c}{\# Params}  & \multicolumn{1}{c}{Accuracy(\%)} \\\hline
+%\textbf{Feature Group} & \multicolumn{1}{c}{\# Params}  & \multicolumn{1}{c}{Accuracy (\%)} \\\hline
 %%\feat{POS} & 540,947 & 55.18 \\
@@
       %\hline
- \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy(\%)}	\\				
+ \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy (\%)}	\\				
        \hline %\hline
@@
       %\hline
- \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy(\%)}	\\				
+ \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy (\%)}	\\				
        \hline %\hline
@@
 \begin{itemize}
-\item Arabic speakers use \textnl{a lot} as a single word more often and sometime omit the definite article before nouns and adjectives. 
+\item Arabic speakers use \textnl{alot} as a single word more often and sometime omit the definite article before nouns and adjectives. 
 \item German authors use hyphens more frequently, probably due to compounding in their native language. They also tend to substitute the letter \textnl{y} with \textnl{z} and vice versa.

### 2013-06-04 poster/poster.tex
wrong font
final model feature count
brown only

@@
 \item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings.% as well as the word position where the error occurred.
-\item[\feat{Restore}] Substitutions, deletions and
+\item[Restore] Substitutions, deletions and
   insertions of common words that were restored with an $n$-gram LM.
@@
       %\hline
- \multicolumn{1}{c}{} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
+ \multicolumn{1}{c}{\emph{true}$\downarrow$} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
  & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
@@
        \hline %\hline
-\feat{POS} & 540,947 & 55.18 \\
+\feat{POS only} & 540,947 & 55.18 \\
 + \feat{FreqChar} & 1,036,871 & 79.55 \\ 
@@
 \qquad + \feat{Brown} & 5,664,461 & 81.09 \\
+\feat{Brown only} & 1,240,420 & 72.26 \\
 			\hline%\hline
@@
 \textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
-\textsc{full model} & - & {\bf 84.55} \\
+\textsc{full model} & 8,312,205 & {\bf 84.55} \\
 
